# Categories {#categorychapter}

The ninety topics we've looked at so far are informative, but they are arguably too detailed to provide a useful big-picture view of what's happening in philosophy. To do that I divided up the ninety topics into 12 categories. Or, to be more precise I divided eighty of them up into categories, and the other ten were split between two categories. I'll return in the next chapter to how this division was made, and in particular how the splitting was done. For now, let's look at the categories and then look at their representation in the literature over time.

```{r category_setup_local, fig.height=12, fig.width = 10}
# Burp
require(readr)
the_categories <- read_csv("category-summary-22031848-90-r15.csv")

category_table <- tribble(
  ~topic, ~subject, ~category, ~keywords
)

for (j in 1:90){
  relevant_keywords <- distinctive_topics %>%
    slice(((j-1)*15+1):((j-1)*15+5))
  keywords_for_table <- paste(relevant_keywords$term, sep=", ", collapse = ", ")
  if (!the_categories$cat_num[j] == 13){
    category_table <- category_table %>%
      add_row(topic = j, 
              category = fcap(str_to_lower(the_categories$cat_name[j])), 
              subject = fcap(the_categories$sub_lower[j]), 
              keywords = keywords_for_table)
  }
  if (the_categories$cat_num[j] == 13){
    temp_category_tibble <- tibble(
      topic = (j*100+1):(j*100+2))
    temp_category_tibble <- temp_category_tibble %>%
      inner_join(the_categories, by = "topic")
    temp_category <- fcap(paste(str_to_lower(temp_category_tibble$cat_name), sep = "/", collapse = "/"))
    category_table <- category_table %>%
      add_row(topic = j, 
              category = temp_category,
              subject = fcap(the_categories$sub_lower[j]), 
              keywords = keywords_for_table)
    
  }
}

kable(category_table,  
	col.names = c("Topic", "Subject", "Category", "Keywords"))
```

## Graphs

First, let's look at how many articles are in each category in each year. I'll say an article is "in" a category if the probability the model gives to the article being from that category is greater than the probability it gives to the article being from any other category. And the probability an article is from a category is just the sum of the probability that it is from one of the topics (or subtopics) that make up the category. (What's a subtopic? I'll get to that in [the next chapter](#subtopics-section).)

```{r category-count, fig.cap = "Number of articles in each of the twelve categories over time.", fig.alt = alt_text}
# Burp
category_count <- category_gamma %>%
  group_by(document, cat_name) %>%
  dplyr::summarise(n = sum(gamma)) %>%
  top_n(1, n) %>%
  ungroup() %>%
  select(document, category = cat_name) %>%
  inner_join(articles, by = "document") %>%
  select(document, year, category) %>%
  group_by(year, category) %>%
  dplyr::summarise(n = n_distinct(document)) %>%
  ungroup() %>%
  complete(year, category, fill = list(n= 0))

category_count_graph <- ggplot(category_count, aes(x = year, y = n, color=fcap(str_to_lower(category)), group=fcap(str_to_lower(category)))) +
    labs(x = element_blank(), y = "Number of Articles") +
    scale_y_continuous(expand = expansion(mult = c(0.01, .03)),
#                     minor_breaks = scales::breaks_pretty(n = 15),
                      minor_breaks = 10 * 1:20,
#                     breaks = scales::breaks_pretty(n = 3)) +
                      breaks = 50 * 1:3) +
    scale_x_continuous(expand = expansion(mult = c(0.01, .03)),
                     minor_breaks = 10 * 1:201,
                     breaks = 40 * 1:50) +
    spaghettistyle +
    theme(legend.title = element_blank(), legend.position = "bottom")  
  
category_count_graph +  
  geom_point(size = 0.5, alpha = 0.5)

alt_text <- "A scatterplot showing the raw number of articles in each year in each of the 12 categories. The graph is too busy to see much usable information. The data for this graph, and the next, are in Table C.1 in appendix C."
```

That's a lot of dots, and I'm not sure it's easy to see a trendline in there. Let's add some automatic trendlines to see if it's any clearer.

```{r category-count-trends, fig.cap = "Number of articles in each of the twelve categories over time (with trendlines).", fig.alt = alt_text}
# Burp
category_count_graph + 
  geom_point(size = 0.5, alpha = 0.2) +
  geom_smooth(se=F, method = "loess", formula = "y ~ x", size = 0.2)

alt_text <- "A version of the previous scatterplot with trendlines added. The pattern in the trendlines is described in the text."
```

That's a bit clearer, but only a bit. Most categories are growing, which isn't surprising because there are more and more articles each year. Philosophy of science starts rising early and keeps on rising. Ethics shoots up in the postwar years, and gets to a high point around 1980. Mind grows, but loses rank. metaphysics and epistemology both grow, though metaphysics's growth comes earlier. Logic and mathematics is strongest in mid-century. History gets smaller over time. (This certainly tells us more about the journals than the field.) And idealism grows until at least World War I, then falls dramatically.

In principle it's better to do this with probabilities rather than just these counts though, to reflect the fact that the model itself is probabilistic. So next I'll show the expected number of articles in each category in each year. That is, for each category and year, I'll take the sum across all articles from that year of the probability that the article is in that category. And the probability that an article is in a category is just the sum of the probabilities of it being in the topics and subtopics that make up the category.

```{r category_graph_setup}

category_gamma_graph <- category_gamma %>%
  inner_join(articles, by = "document") %>%
  select(journal, year, category = cat_name, gamma) %>%
  group_by(journal, year, category) %>%
  dplyr::summarise(g = sum(gamma)) %>%
  ungroup() %>%
  complete(journal, year, category, fill = list(g = NA))

category_year <- category_gamma_graph %>%
  group_by(category, year) %>%
  dplyr::summarise(y = sum(g, na.rm=TRUE))

year_denominator <- category_gamma_graph %>%
  group_by(year) %>%
  dplyr::summarise(d = sum(g, na.rm = TRUE))

category_frequency <- inner_join(category_year, year_denominator, by = "year") %>%
  mutate(f = y / d)
```

```{r category-weight-graph,  fig.cap = "Weighted number of articles in each of the twelve categories over time", fig.alt = alt_text}
category_weight_graph <- ggplot(category_year, aes(x = year, y = y, color=category, group=category)) +
    labs(x = element_blank(), y = "Number of Articles") +
    scale_y_continuous(expand = expansion(mult = c(0.01, .03)),
#                     minor_breaks = scales::breaks_pretty(n = 15),
                      minor_breaks = 10 * 1:20,
#                     breaks = scales::breaks_pretty(n = 3)) +
                      breaks = 50 * 1:3) +
    scale_x_continuous(expand = expansion(mult = c(0.01, .03)),
                     minor_breaks = 10 * 1:201,
                     breaks = 40 * 1:50) +
    spaghettistyle +
    theme(legend.title = element_blank(),
          legend.position = "bottom")  

category_weight_graph + 
  geom_point(size = 0.5, alpha = 0.5)

alt_text <- "A scatterplot showing the weighted number of articles in each year in each of the 12 categories. The graph is only a bit clearer than figure 4.1. The data for this graph, and the next, are in Table C.2 in appendix C."

```

That's also a bunch of dots, though interestingly the trends are more visible without trend lines. Let's see what happens when we add the trend lines back in.

```{r category-weight-graph-trendlines, fig.cap = "Weighted number of articles in each of the twelve categories over time (with trendlines).", fig.alt = alt_text}
category_weight_graph + 
  geom_point(size = 0.5, alpha = 0.2) +
  geom_smooth(se=F, 
              method = "loess", 
              formula = "y ~ x",
              size = 0.2)

alt_text <- "A version of the previous scatterplot with trendlines added. The pattern in the trendlines is described in the text."
```

That's pretty similar to the other trendline graph. The big difference is that the lines are more compressed. (This is most visible in the scales.) But the rank at any given time is fairly similar.

The big challenge here is seeing which rises are due to a category getting more prominent, and which are due to the field getting bigger. So let's take that graph and divide all the values by the number of articles in a given year. What we end up with, for each year-category pair, is the average probability an article from a year falls into that category. The numbers are thrown off a fair bit by the presence of a lot of psychology articles in _Mind_ before 1900, so I'll start in 1900.

```{r category-frequency-graph, fig.cap = "Proportion of articles in each category each year.", fig.alt = alt_text}
category_frequency_graph <- ggplot(filter(category_frequency, year > 1899), 
                                   aes(x = year, y = f, color=category, group=category)) +
    labs(x = element_blank(), y = "Proportion of Articles") +
    scale_y_continuous(expand = expansion(mult = c(0.01, .03)),
#                     minor_breaks = scales::breaks_pretty(n = 15),
                      minor_breaks = 0.025 * 1:20,
#                     breaks = scales::breaks_pretty(n = 3)) +
                      breaks = 0.1 * 0:5) +
    scale_x_continuous(expand = expansion(mult = c(0.01, .03)),
                     minor_breaks = 10 * 1:201,
                     breaks = 40 * 1:50) +
    spaghettistyle +
    theme(legend.title = element_blank(),
          legend.position = "botto") 

category_frequency_graph + geom_point(size = 0.5, alpha = 0.5)  + theme(legend.title = element_blank())

alt_text <- "A scatterplot showing the weighted frequency of articles in each year in each of the 12 categories. The graph is quite a bit clearer than the earlier scatterplots, and its shape is described in the text below. The data for this graph, and the next, are in Table C.3 in appendix C."
```

It's striking how many trendlines are already visible, but it's clearer with actual trendlines added.

```{r category-frequency-graph-trendlines, fig.cap = "Proportion of articles in each category each year (with trendlines).", fig.alt = alt_text}
category_frequency_graph + 
  geom_point(size = 0.5, alpha = 0.2) + 
  geom_smooth(se=F, method = "loess", formula = "y ~ x", size = 0.2) 

alt_text <- "A version of the previous scatterplot with trendlines added. The pattern in the trendlines is described in the text."
```

And it's really striking how many of the graphs are relatively simple to describe.

- Aesthetics is always low, though it's high point is midcentury.
- Epistemology is almost invisible until 1950, then rises linearly afterward.
- Ethics has a low equilibrium before 1930, a high equilibrium after 1970, and rises rapidly between those points.
- History of philosophy falls from 1930 to 2000, though maybe it has stopped falling.
- Idealism falls rapidly until it hits 0 around 1980. (Though note that this is a consequence of my excluding the nineteenth-century data points - it arguably rises in the early twentieth-century.)
- Logic and mathematics reaches a high point around 1955, with a striking rise before then and fall afterwards.
- Metaphysics has a steady base through the early 1960s, and then a steady rise after that. (This is not remotely in keeping with my prior view about metaphysics in the journals, and we'll come back to how plausible this is.)
- Apart from a small blip around 1930, philosophy of language has a low equilibrium before 1950, and a higher equilibrium afterwards.
- Philosophy of mind falls as the psychology articles gradually fade (and the relative size of _Mind_ fades) but is very constant from 1940 or so onwards.
- Philosophy of religion is very small, but probably gradually falling.
- Philosophy of science rises rapidly through 1940, then hits an equilibrium, then rises rapidly again after 1970.
- Social and political has a peak around 1920, then a dip and another peack 1940, then gradually fades. (Again, this is not remotely like what I expected, though the explanation isn't that hard.)

In the next chapter I'll go over how the categories were constructed, which in turn will explain some of these trends. But some of them are just interesting facts about the nature of philosophy in these twelve journals.

It might be easier to see these twelve categories separated out.

```{r category-frequency-graph-facet, fig.cap = "Proportion of articles in each category (with facets).", fig.alt = alt_text}
tt <- filter(category_frequency, year > 1899)
category_graph_labels <- tt %>%
  group_by(category) %>%
  summarise(year = median(year)) %>%
  mutate(f = max(tt$f) * 1.2)
ggplot(tt, 
       aes(x = year, y = f, color=category, group=category)) +
  geom_text(data = category_graph_labels,
            mapping = aes(label = category),
            vjust = "inward", 
            hjust = "inward",
            fontface = "bold", 
            size = 3) +
  labs(x = element_blank(), y = "Proportion of Articles", title = "Proportion of Articles in Each Category Per Year") +
  geom_point(size = 0.15) + 
  facet_wrap(~category, ncol=3) +  
  scale_x_continuous(expand = expansion(mult = c(0.05, 0.05))) +
  scale_y_continuous(expand = expansion(mult = c(0, .03))) +
  facetstyle

alt_text <- "A version of Figure 4.5 where each category is shown on a separate graph. The data is in Table C.4 in appendix C, and the trends are described in the text below."
```

It's really striking how continuous these graphs are. This is not something that's programmed in—we're just seeing one data point after another rather than trendlines. The numbers here are sums across journals, and across topics/subtopics. And within each of those components, there is nothing like this continuity. But the large year-to-year variation mostly washes away at the category level.

## Split Topics

Normally at this point I would include a long discussion of the methodology that produced graphs like this. But the methodology is so complicated that I put it in a whole separate [chapter](#sortingchapter). But there is one point I need to clarify before discussing the individual topics.

Several topics didn't easily fit into one or other category. For several of them, I just had to choose the least bad category to put it in. But for some, it turned out to be possible to split the topic into two **subtopics**, and categorize the subtopics. I somewhat arbitrarily imposed a limit on myself of doing this ten times, so the following ten topics got broken into two subtopics each.

```{r sub-topic-list}
subtopic_table <- the_categories %>%
  filter(cat_num == 13 | topic > 100)
subtopic_function <- function(x){
  tibble(a = subtopic_table$subject[x], b = subtopic_table$subject[2*x+9], c = subtopic_table$subject[2*x+10])
}
subtopic_kable <- lapply(1:10, subtopic_function) %>% bind_rows()
kable(subtopic_kable, 
	col.names = c("Original Topic", "First Subtopic", "Second Subtopic"))
```

So we end up with one hundred topics and subtopics to classify; the eighty original topics that weren't split, and the twenty subtopics just generated. How I split them up is a bit of a saga, and I'll run through it in the next [chapter](#sortingchapter).

In what remains of this chapter, I'll go one by one through eight of the twelve topics. For each topic, I'll look at its trends, and how those are generated by its constituent topics, and by the twelve journals. I'm leaving out four categories from this discussion.

- Idealism is a single topic, and I've already discussed it.
- Aesthetics and philosophy of religion are just a pair of topics, and there isn't much to say that isn't in the discussion of their constituent parts.
- I'm doing a deeper look at epistemology in [a later chapter](#epistemologychapter), so there's no need for another discussion here.

```{r tables_for_category_individual_sections}
# Burp
category_section_main_tibble <- category_gamma %>%
  inner_join(articles, by = "document") %>%
  select(document, topic, gamma, journal, year)

category_by_topic <- category_section_main_tibble %>%
  group_by(topic, year) %>%
  dplyr::summarise(g = sum(gamma)) %>%
  ungroup() %>%
  inner_join(the_categories, by = "topic") %>%
  select(topic, year, g, category = cat_name, name = subject, name_lower = sub_lower) %>%
  inner_join(year_denominator, by = "year") %>%
  mutate(f = g/d)

journal_denominator <- articles %>%
  select(document, journal, year) %>%
  group_by(journal, year) %>%
  dplyr::summarise(d = n_distinct(document))

category_by_journal <- category_section_main_tibble %>%
  inner_join(the_categories, by = "topic") %>%
  select(document, journal, year, gamma, category = cat_name) %>%
  group_by(category, journal, year) %>%
  dplyr::summarise(g = sum(gamma)) %>%
  ungroup() %>%
  inner_join(journal_denominator, by = c("year", "journal")) %>%
  mutate(f = g/d)  

subtopic.labs <- the_categories$subject
names(subtopic.labs) <- the_categories$topic

category_by_journal$journal <- factor(category_by_journal$journal, levels = journal_order)

```

```{r graph-style-for-categories}
# Burp
cg <- function(cate, cate_num){
  yupper <- max(category_by_journal$f, na.rm=TRUE)

facet_labels <- chap_two_facet_labels %>%
  mutate(year = 1944.5, f = yupper)

facet_labels$journal <- factor(facet_labels$journal, levels = journal_order)

ggplot(data = filter(category_by_journal, category == cate), aes(x = year, y = f))  +
      facetstyle +
      scale_y_continuous(breaks = c(0.25, 0.5),
                       minor_breaks = 0.05 * 1:14) +
      geom_point(size = 0.15, colour = hcl(h = (cate_num-1)*30+15, l = 65, c = 100)) +
      theme(legend.position="none",
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank()) +
      labs(x = element_blank(), y = "Weighted Proportion of Articles") +
      facet_wrap(~journal, ncol = 3) +
    geom_text(data = facet_labels,
            mapping = aes(label = short_name),
            vjust = "inward", 
            hjust = "middle",
            fontface = "bold", 
            size = 3,
            colour = "grey40")
}

cg_alt_text <- function(cate, cate_num){
cate_lower <- str_to_lower(cate)
temp <- category_by_journal %>% 
  filter(category == cate) %>% 
  group_by(journal) 
temp_mean <- temp %>% 
  summarise(m = percent(mean(f), accuracy = 0.1))
temp_max <- temp %>% 
  slice_max(f, n = 1) %>% 
  mutate(maxf = percent(f, accuracy = 0.1)) %>% 
  select(journal, maxf, maxyear = year)
temp_min <- temp %>% 
  slice_min(f, n = 1) %>% 
  mutate(minf = percent(f, accuracy = 0.1)) %>% 
  select(journal, minf, minyear = year)
temp_main <- temp_mean %>% 
  left_join(temp_max, by = "journal") %>% 
  left_join(temp_min, by = "journal")
  ttt <- paste0(
    "Twelve scatterplots showing which percentage of the articles in each journal in each year are in the category ",
    cate_lower,
    ". A brief summary of the data follows. "
  )
  for (ijk in 1:12){
    ttt <- paste0(ttt,
                  "In an average year in ",
                  temp_main$journal[ijk],
                  ", ",
                  temp_main$m[ijk],
                  " of the articles are in the category ",
                  cate_lower,
                  ". ",
                  str_to_sentence(cate),
                  " is most prevalent in ",
                  temp_main$journal[ijk],
                  " in ",
                  temp_main$maxyear[ijk],
                  " when it accounts for ",
                  temp_main$maxf[ijk],
                  " of the articles in the journal. And it is least prevalent in ",
                  temp_main$minyear[ijk],
                  " when it accounts for ",
                  temp_main$minf[ijk],
                  " of the articles in the journal. "
                  )
  }
  ttt
}

cgt <- function(cate, cate_num){

yupper <- max(filter(category_by_topic, category == cate)$f, na.rm = TRUE)

facet_labels <- category_by_topic %>%
  group_by(topic, name, category) %>%
  summarise(f = 0.065) %>%
  mutate(year = 1944.5)

print(
  ggplot(data = filter(category_by_topic, category == cate, f < 0.0601, year > 1900), aes(x = year, y = f))  +
    geom_text(data = filter(facet_labels, category == cate),
            mapping = aes(label = name),
            vjust = "inward", 
            hjust = "middle",
            fontface = "bold", 
            size = 3,
            colour = "grey40") +
    facetstyle +
    geom_point(size = 0.15, colour = hcl(h = (cate_num-1)*30+15, l = 65, c = 100)) +
    theme(legend.position="none",
          panel.grid.minor = element_line(color = "grey90", size = 0.03),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank()) +
    labs(x = element_blank(), y = "Weighted Proportion of Articles") +
    facet_wrap(~topic, ncol = 3) +
    scale_y_continuous(breaks = c(0.02, 0.04),
                       minor_breaks = 0.005 * 1:11,
                       lim = c(0, 0.0651))
)

# Table of Data Points that are excluded by the topic graph
if (max(filter(category_by_topic, category == cate, year > 1900)$f > 0.0601)){
print(
     kable(filter(category_by_topic, category == cate, f > 0.0601, year > 1900) %>%
          select(name_lower, year, f) %>%
          mutate(f= round(f, 4)) %>% 
          mutate(name_lower = fcap(name_lower)),
        caption = paste0("Points excluded from topic graph for ",str_to_lower(cate)),
        col.names = c("Subject", "Year", "Frequency"))
)
}

}

cgt_alt_text <- function(cate, cate_num){
cate_lower <- str_to_lower(cate)
temp <- category_by_topic %>% 
  filter(category == cate) %>% 
  filter(year > 1900) %>% 
  group_by(name_lower) 
temp_mean <- temp %>% 
  summarise(m = percent(mean(f), accuracy = 0.1))
temp_max <- temp %>% 
  slice_max(f, n = 1) %>% 
  mutate(maxf = percent(f, accuracy = 0.1)) %>% 
  select(name_lower, maxf, maxyear = year)
temp_main <- temp_mean %>% 
  left_join(temp_max, by = "name_lower")
  ttt <- paste0(
    nrow(temp_main),
    " scatterplots showing which percentage of the articles in all journals in each year from 1900 onwards are in the each of the topics category ",
    str_to_lower(cate),
    ". A brief summary of the data follows. "
  )
  for (ijk in 1:nrow(temp_main)){
    ttt <- paste0(ttt,
                  "In an average year, ",
                  temp_main$m[ijk],
                  " of the articles are in the ",
                  temp_main$name_lower[ijk],
                  "topic. ",
                  str_to_upper(str_sub(temp_main$name_lower[ijk],1,1)),
                  substring(temp_main$name_lower[ijk],2),
                  " is most prevalent in ",
                  temp_main$maxyear[ijk],
                  " when it accounts for ",
                  temp_main$maxf[ijk],
                  " of the articles in all journals. "
                  )
  }
  ttt
}
```

## Ethics {#ethics-category-section}

```{r ethics-journals, fig.cap = "Proportion of each journal's yearly publications in Ethics.", fig.alt = alt_text}
cg("Ethics", 3)
alt_text <- cg_alt_text("Ethics", 3)
```

There are a lot of ethics articles in _Ethics_. That's not surprising. But what's really the story here is that the proportion of _Ethics_ that is devoted to ethics keeps rising. The two most recently added journals, _Noûs_ and _Philosophy and Public Affairs_, respectively have good and great ethics coverage, so that helps the upward trend as well. But the big story here is the consolidation of the key specialist journal. We will see this trend a few times as we move along.

Let's look at how this is broken up into individual topics. I'm going to do a graph like this for every category, and they will all have the following restrictions.

- The nineteenth-century is excluded, and the years start in 1901.
- The Y-axis is capped at 0.06, i.e., 6 percent, and if there are points that are thereby excluded, I'll list them separately in a table.

Both restrictions are motivated by the problems that affected the frequency graphs in the previous chapter. (What I'm doing here is a topic-by-topic version of the [weighted frequency of articles]({#graph-wfa}) graph.) There isn't enough diversity in the early years, so some topics can be 10, 20, even 30 percent of the total. And there isn't a good way to represent those numbers on a graph while also making the differences between 1 percent and 3 percent (which is what we care most about here) particularly visible. So I'll just list separately the problematic data points.

```{r ethics-topics, fig.height=10.2, fig.cap = "Topics in ethics.", fig.alt = alt_text}
cgt("Ethics", 3)
alt_text <- cgt_alt_text("Ethics", 3)
```

A quick note about the he subtopic "OLP Ethics". The "OLP" here is for ordinary language philosophy. So this subtopic is the ethics part of ordinary language philosophy. I'm moderately confident that this really is part of ethics—it includes papers like Philippa Foot's "[Moral Beliefs](https://philpapers.org/rec/FOOVB)". But I'm not 100 percent sure about this, since it includes a lot of things that don't feel exactly like ethics papers as we'd currently understand that. In general, ordinary language philosophy makes this kind of analysis hard.

Note how there are a few topics that peak one after the other: first value, then promises and imperatives, then duties, and now norms. But none of this rise and fall is visible in the overall graph, which is fairly steady. Some of these rises and falls comes from changing interests among folks in the field, but some I think comes from simply changes in fashionable terminology.

## History {#history-category-section}

```{r history-journals, fig.cap = "Proportion of each journal's yearly publications in history of philosophy.", , fig.alt = alt_text}
cg("History of Philosophy", 4)
alt_text <- cg_alt_text("History of Philosophy", 4)
```

None of these lines seem to be trending up, and several of them are trending down. But there are differences in the ways that they are trending.

- _Ethics_ is a slow, steady decline.
- _Journal of Philosophy_ is a very rapid decline over the 1960s, between a high equilibrium before that, and a much lower equilibrium after.
- _Mind_ falls off a cliff around World War II, around the same time Ryle takes over.
- _Philosophy and Phenomenological Research_ falls away around 1990, as they stop taking quite as seriously the part of their name that says "phenomenological". (I don't know how closely this tracks with Ernest Sosa becoming editor of PPR.)

So part of what's going on is what I mentioned in the previous section. Specialist journals are focusing more on their specialty, and this means doing less of everything else. And in part this feels like the long influence of Gilbert Ryle. This might seem odd given that Ryle published in history of philosophy, but there is some independent evidence of this. This is from an article his successor as _Mind_ editor, D. M. Hamlyn, [wrote about Ryle's editorship](https://www.jstor.org/stable/23955672?seq=5#metadata_info_tab_contents).

> [Ryle] said, for example, that, except for Greek Philosophy, he tended to not accept papers on the history of philosophy, and he also said something about what was normally the desirable maximum length for papers. I must say that I found what he had to say on the first point rather odd, though he was absolutely right on the second. [@Hamlyn2003, 5-12]

Whatever Hamlyn thought, it doesn't seem to have affected the publications much. You can't see his ascension (in 1971) in the data here. And I think this decision of Ryle's had a large impact on the role of journal articles in history of philosophy. (Though note Hamlyn says in that paper that Ryle left him a backlog of 2 years' material to publish. So any break would be 1973 not 1971. Both these facts, that _Mind_ was only publishing its backlog in 1972 and 1973, and that they were still papers accepted by Ryle, are quite interesting in the context of the differences in citation rates between _Mind_ and its US counterparts in those years. But that's a story for another study.)

```{r history-topics, fig.height=6.2, fig.cap = "Topics in history of philosophy.", fig.alt = alt_text}
cgt("History of Philosophy", 4)
alt_text <- cgt_alt_text("History of Philosophy", 4)
```

Two things jump out here. 

One is that when history of philosophy was a major part of the journals, it was driven by the weird mix from [other history](#topic04), not the big names. Remember that the paradigm article from Topic 4 was about James Marsh. 

The other is that [Dewey and pragmatism](#topic05) is also a big part of the story, at least when history is prominent in the journals.

But note that both of these things suggest that to some extent the strength of history before World War II is a touch overstated. Other History includes a bunch of papers that are, if history, very much the first draft of history. For example, for several decades _Philosophical Review_ published an annual piece on philosophy in France, usually written by André Lalande. (A bunch of these papers can be accessed [via PhilPapers](https://philpapers.org/s/%22Philosophy%20in%20France%22%20Lalande), but I haven't looked at many of them personally.) It's kind of history—it surveys what has happened in a place in a historical period. It's just that the period was, you know, the year that just passed. So not really that historical. All of these articles are classed as history by the algorithm. That doesn't explain what happened with _Mind_, of course, but there is stuff there that is only history for want of somewhere else to put it.

And while many of the pragmatism papers are genuinely history papers—they are about works by Dewey several decades after those works were written—some of them are simply works of pragmatist philosophy. (And of course Dewey is still alive, and even publishing, into the 1940s. I think it's possible to do historical work on a figure while they are still alive, but it's a bit odd.)

So I don't think we should think there was really a golden age for publishing history of philosophy in these journals that has now ceased. They did publish things that were historical. And papers on Marsh or on Geulincx are really a kind of history that we just don't see in the current journals. Maybe we need to bring back that kind of history of philosophy. (As I'll discuss at the [end of the book](#imprint-section), there is some evidence that we are bringing that kind of history back.)

## Logic and Mathematics


```{r lm-journals, fig.cap = "Proportion of each journal's yearly publications in logic and mathematics.", fig.alt = alt_text}
cg("logic and mathematics", 6)
alt_text <- cg_alt_text("Logic and Mathematics", 6)
```

The story of this category is a rise until midcentury and a fall afterwards. The journals start to give us a few clues as to what happened.

- _Analysis_ starts off being very welcoming to logic and mathematics—so much so that it messes up the scales for these graphs a bit—but gets progressively less so over time.
- _Noûs_ follows the same pattern.
- _Mind_ under Hamlyn really stops doing any of this kind of work, though it returns in a hurry once Hamlyn leaves.
- _Philosophy of Science_ moves strongly away from doing logic and mathematics work. And given the number of papers _Philosophy of Science_ publishes in the 1990s and 2000s, this affects the numbers a lot.

So part of the story here, perhaps a large part, is a familiar refrain. The specialist journals are getting more specialist, and this is crowding out other things. But the downward trajectory in _Analysis_ and _Noûs_ matters too. Let's look by topics.

```{r lm-topics, fig.cap = "Topics in Logic and Mathematics", fig.alt = alt_text}
cgt("Logic and Mathematics", 6)
alt_text <- cgt_alt_text("Logic and Mathematics", 6)
```

That makes a bit clearer what happened. Two topics associated with positivism—[definitions](#topic06) and [verification](#topic15)—are in the category. And they peaked in midcentury and then fell.

They peaked at slightly different times, which I wouldn't have expected. I guess a lot of the work in definitions is really trying to make positivism work, by getting a working account of definitions. And once verification itself becomes a topic, it's because people are starting to think that the verification principle doesn't have a defensible disambiguation. It's not so much logic fell away, as that _logical_ positivism did. And we knew that would happen.

It's only up to 2 percent, but there is an interestingly steady rise in work on theories of [truth](#topic59). These play an important role in contemporary theories of logic, especially in motivating nonclassical theories. The optimistic take on this category is that the topics that have fallen are now basically at 0, so they can't fall farther, while other topics are steadily rising. I'm not sure I buy that—I suspect we'll see more falls if we extend this study beyond 2013—but it's one reason for optimism.

## Metaphysics {#metaphysics-category-section}

```{r metaphysics-journals, fig.cap = "Proportion of each journal's yearly publications in Metaphysics", fig.alt = alt_text}
cg("Metaphysics", 7)
alt_text <- cg_alt_text("Metaphysics", 7)
```

The short version is that metaphysics is at worst flat in every journal, and rising rapidly in _Analysis_, _Philosophical Quarterly_ and _Philosophy and Phenomenological Research_. That's fine, but shouldn't we see positivism showing up somewhere that put downward pressure on metaphysics at least somewhere? If that happens, it isn't visible in the journal-level data. What happens at the topic-level?

```{r metaphysics-topics, fig.height = 6.2, fig.cap = "Topics in Metaphysics", fig.alt = alt_text}
cgt("Metaphysics", 7)
alt_text <- cgt_alt_text("Metaphysics", 7)
```

So there are two big topics—[modality](#topic80), and [composition and constitution](#topic89)-that only take off after positivism goes away. The same is probably true of [causation](#topic54) as well, but it's much smaller. I was surprised that causation was so much smaller than the other very modern categories; maybe that's in part because some of the causation work ended up getting classified as philosophy of science.

But we still haven't answered the question about where positivism shows up. I thought that the graph here would be U-shaped, with lots of metaphysics on either side of a positivism-driven dip in the middle. We can recreate that gap if we declare that all the work in idealism is really metaphysics.

```{r metaphysics-and-idealism-frequency, fig.cap = "Proportion of each year's articles that are in idealism or metaphysics.", fig.height = 5, fig.alt = alt_text}
cate_num <- 7
m_and_i_table <- category_frequency %>%
  filter(category == "Metaphysics" | category == "Idealism") %>%
  group_by(year) %>%
  dplyr::summarise(f = sum(f))

m_and_i_graph <- ggplot(data = m_and_i_table, aes(x = year, y = f)) +
      spaghettistyle +
      geom_point(size = 0.5, colour = hcl(h = (cate_num-1)*30+15, l = 65, c = 100)) +
      theme(legend.position="none") +
      ylim(0, 0.4) +
      labs(x = element_blank(), y = "Weighted Proportion of Articles")
  
m_and_i_graph

alt_text <- "A scatterplot showing the proportion of articles that are in either idealism or metaphysics. It starts around 10%, rises to over 30% in the early 20th century, then falls very linearly back to around 10% by 1940. It is then fairly stable, with perhaps a small upwards trend over the last 50 years that isn't obviously significant."
```

That's more like what I expected, though the postpositivism rise is much smaller than the prepositivism fall. It obviously looks different if using counts rather than proportions.

```{r metaphysics-and-idealism-count, fig.cap = "Weighted number of each year's articles that are in idealism or metaphysics.", fig.height = 5, fig.alt = alt_text}
m_and_i_count_table <- category_frequency %>%
  filter(category == "Metaphysics" | category == "Idealism") %>%
  group_by(year) %>%
  dplyr::summarise(f = sum(y))

m_and_i_count_graph <- ggplot(data = m_and_i_count_table, aes(x = year, y = f)) +
      spaghettistyle +
      geom_point(size = 0.5, colour = hcl(h = (cate_num-1)*30+15, l = 65, c = 100)) +
      theme(legend.position="none") +
      labs(x = element_blank(), y = "Weighted Number of Articles")
  
m_and_i_count_graph

alt_text <- "The same graph as the previous one, but showing the number of articles, not the proportion of articles, in Idealism or Metaphysics. It is a fairly linear trajectory upwards, getting to around 50 papers/year by the end of the study."
```

And now we're back to a steady rise, with no obvious place to locate the rise of positivism.

I think the big story here is that positivism has much less impact on the journals thanoneyou might think from the standard story about the history of twentieth century philosophy. If positivists are given credit for killing idealism, then positivism has an enormous influence. But I'm not sure what the case is for that. It's not like Moore was a card-carrying positivist, and he surely had something to do with the downfall of idealism.

Anyway, let's keep track of this when looking at subsequent topics, because it would be very surprising to see no impact from positivism on the literature.

## Philosophy of Language

```{r language-journals, fig.cap = "Proportion of each journal's yearly publications in Philosophy of Language", fig.alt = alt_text}
cg("Philosophy of Language", 8)
alt_text <- cg_alt_text("Philosophy of Language", 8)
```

There isn't much trend there. Within _Analysis_ I guess there is a downward trend, though it's so random before its wartime hiatus that it's hard to say. _Philosophical Review_ starts publishing philosophy of language articles in the 1940s then especially in the 1950s. (This is probably connected to Norman Malcolm moving to Ithaca.) Afterwards there is a bit of year-to-year variation, largely because the Review publishes so few articles. Before Ryle takes over there isn't a lot of philosophy of language in _Mind_, then it is fairly steady apart from a blip upward in the 1990s. But otherwise there isn't much trend here to speak of. Let's instead look at the topics.


```{r language-topics, fig.height = 6.2, fig.cap = "Topics in Philosophy of Language", fig.alt = alt_text}
cgt("Philosophy of Language", 8)
alt_text <- cgt_alt_text("Philosophy of Language", 8)
```

That's more interesting. Four of the topics are almost absent before 1940. A fifth, centered around [On "Denoting](https://philpapers.org/rec/RUSOD)", has a flurry of early century activity, then picks back up again in the 1950s. All five of them continue to be important to the present day, though a few of them look slightly down from their peaks.

But the dominant theme here is Wittgensteinian philosophy of language. It has a remarkable rise and then an equally remarkable fall. What surprises me is how much work on this topic the model finds pre-1900. It could just be noise—we're talking at most 2 percent of a small number of articles. But the model doesn't think that Fregean or Quinean philosophy of language turns up in these articles, so it's a bit interesting that it sees some Wittgensteinian work there.

The rise and fall of Wittgensteinian philosophy of language is not symmetric. The rise took away from other parts of philosophy, but when the fall happened the interest simply shifted to other areas in philosophy of language. The result was that philosophy of language was stronger afterward than before, though the work that ended up being central was not the work that made philosophers take philosophy of language seriously.

There would be more topics here, and the overall graph would trend more sharply upwards, except the model itself thought that some topics that could have been in philosophy of language are better placed in logic and mathematics. I'll come back to that in the next chapter.

## Philosophy of Mind

```{r mind-journals, fig.cap = "Proportion of each journal's yearly publications in Philosophy of Mind", fig.alt = alt_text}
cg("Philosophy of Mind", 9)
alt_text <- cg_alt_text("Philosophy of Mind", 9)
```

Again, it's hard to see much of a trend here. _Mind_ stops publishing work that is (by contemporary standards) more psychology than philosophy, and that leads to a bit of a fall. Then there is an odd fall in the 1990s, simultaneous with an upsurge in how many philosophy of language papers _Mind_ publishes. But otherwise it's like every journal decided at its foundation what proportion of its space will go to philosophy of mind, and it has stuck to that pretty closely ever since. Just what topics in philosophy of mind that they've covered is much less stable. 

```{r mind-topics, fig.height = 10.2, fig.cap = "Topics in Philosophy of Mind", fig.alt = alt_text}
cgt("Philosophy of Mind", 9)
alt_text <- cgt_alt_text("Philosophy of Mind", 9)
```

The [psychology](#topic01) topic, which I had always associated with _Mind_ pre-1900, hangs around into the 1930s. It doesn't make up a big portion of what _Mind_ does in the twentieth century, but it is an important part of the early years of _Philosophical Review_. Some of the other topics are arguably papers that could just have easily been classified with Psychology. That's true for the handful of [color/colour](#topic40) papers in the 1880s and the pre-1900 work on [emotions](#topic28). It's also somewhat true of the early work on [self-consciousness](#topic12), though some of that work is also idealist influenced.

I've already talked about the [physicalism](#topic09) topic at some length and won't repeat it here; this was a very large surprise.

OLP mind is the part of [ordinary Language philosophy](#topic24) dealing with philosophy of mind. Unlike the ethics part of ordinary language philosophy, the model thinks this was just picking up on an existing trend, rather than building something wholly new.

The more recent topics are not too surprising. Thankfully journals are now publishing more work on [cognitive science](#topic87). I would have guessed that the graph for [minds and machines](#topic58) would have started earlier, and stayed higher, than the graphs for conceivability arguments and for [concepts](#topic78), but it's not too surprising.

The Freud subtopic is tiny, but that's in part because some of the Freud articles got slid over into [intention](#topic48). I don't know what the model was thinking there, but it didn't affect the overall category graphs.

## Philosophy of Science

```{r science-journals, fig.cap = "Proportion of each journal's yearly publications in Philosophy of Science", fig.alt = alt_text}
cg("Philosophy of Science", 11)
alt_text <- cg_alt_text("Philosophy of Science", 11)
```

The trend here is fairly simple, and it resembles what I said about the [ethics category](#ethics-category-section). The specialist journals have become more specialized, and the other journals haven't changed a lot. Now in this case, that's in part because most of the journals were doing very little of (what we'd now call) philosophy of science. I think they would have disagreed with that description; some of what I've called metaphysics, and some of what I've called logic and mathematics, they would have called philosophy of science. But by modern lights they weren't doing very much of it, and they still aren't. The big, and important, exception is _Journal of Philosophy_, and it hasn't cut back its philosophy of science coverage.

```{r science-topics, fig.height = 12.2, fig.cap = "Topics in Philosophy of Science", fig.alt = alt_text}
cgt("Philosophy of Science", 11)
alt_text <- cgt_alt_text("Philosophy of Science", 11)
```

The model carves up the philosophy of science topics very finely, and so it's hard to eyeball a lot of trends. [Quantum](#topic66) goes up rapidly to a peak in the 1990s. (I did not realise it wasn't still growing.) [Evolutionary biology](#topic82) starts later, and maybe is still growing. The [realism](#topic67) wars of the 1980s didn't quite end, but maybe they are fading away. On the other hand, there is more attention being paid to [models](#topic88), and some of that is related to the realism wars.

## Social and Political

```{r social-journals, fig.cap = "Proportion of each journal's yearly publications in Social and Political Philosophy", fig.alt = alt_text}
cg("Social and Political", 12)
alt_text <- cg_alt_text("Social and Political", 12)
```

With the exception of _Philosophy and Public Affairs_, the trend seems to be down in every journal. This surprised me a lot. In part this was because the journals stopped publishing work on [history and culture](#topic10). In part it was because the model insisted that [life and value](#topic03), what I thought of as idealist ethics, was really a topic in social and political, not ethics. But in part it was because the study ended before the boom in social and political work in the mid-2010s.

```{r social-topics, fig.cap = "Topics in Social and Political", fig.alt = alt_text}
cgt("Social and Political", 12)
alt_text <- cgt_alt_text("Social and Political", 12)
```

This, I think makes the story about what happened from 1950-2013 make more sense. There was a Rawlsian boom—it shows up clearly in [egalitarainism](#topic65) and [liberal democracy](#topic52). There was even a small bit of interest in [feminism](#topic69). But the drop-off of interest in [Marx](#topic23), and in history and culture, more than made up for it. Given how often I've heard people complain about the excessive amount of Rawlsiana in the late twentieth-century journals, this was rather of a surprise. Of course, you may think that Marxism, and the French Revolution, were slightly more important subjects of detailed study than _A Theory of Justice_, no matter how good a book it is.