--- 
title: "A History of Philosophy Journals"
subtitle: "Volume 1: Evidence from Topic Modeling, 1876-2013"
author: "Brian Weatherson"
date: "Marshall M. Weinberg Professor of Philosophy, University of Michigan, Ann Arbor"
documentclass: book
link-citations: yes
site: bookdown::bookdown_site
description: Building models of the trends in philosophy journals using LDA.
bibliography: topic.bib
nocite: '@*'
always_allow_html: true
---

# Introduction {-}

Placeholder


## Plan {-}
## Publication Information {-}
## Website Instructions {-}
## Acknowledgements {-}
## GitHub {-}
## Replication Instructions {-}
## Volumes {-}

<!--chapter:end:index.Rmd-->


# Methodology {#methodology-chapter}

Placeholder


## Selecting the Twelve Journals
## Selecting the Articles
## Selecting the Words {#stop-words}
## Building a Model
## Choosing the Number of Topics {#choose-topic-number}
## Choosing between whe Models {#model-seed-choice}
## Two Refinements {#refinements-section}
## The Output
## Strengths and Weaknesses {#strengths-and-weaknesses-section}
## Regrets {#regrets-section}

<!--chapter:end:01-methodology.Rmd-->


# The Ninety Topics {#all-90-topics}

Placeholder



<!--chapter:end:02-topics.Rmd-->




<!--chapter:end:topic_comments/topic01.Rmd-->




<!--chapter:end:topic_comments/topic02.Rmd-->




<!--chapter:end:topic_comments/topic03.Rmd-->




<!--chapter:end:topic_comments/topic04.Rmd-->




<!--chapter:end:topic_comments/topic05.Rmd-->




<!--chapter:end:topic_comments/topic06.Rmd-->




<!--chapter:end:topic_comments/topic07.Rmd-->




<!--chapter:end:topic_comments/topic08.Rmd-->




<!--chapter:end:topic_comments/topic09.Rmd-->




<!--chapter:end:topic_comments/topic10.Rmd-->




<!--chapter:end:topic_comments/topic11.Rmd-->




<!--chapter:end:topic_comments/topic12.Rmd-->




<!--chapter:end:topic_comments/topic13.Rmd-->




<!--chapter:end:topic_comments/topic14.Rmd-->




<!--chapter:end:topic_comments/topic15.Rmd-->




<!--chapter:end:topic_comments/topic16.Rmd-->




<!--chapter:end:topic_comments/topic17.Rmd-->




<!--chapter:end:topic_comments/topic18.Rmd-->




<!--chapter:end:topic_comments/topic19.Rmd-->




<!--chapter:end:topic_comments/topic20.Rmd-->




<!--chapter:end:topic_comments/topic21.Rmd-->




<!--chapter:end:topic_comments/topic22.Rmd-->




<!--chapter:end:topic_comments/topic23.Rmd-->




<!--chapter:end:topic_comments/topic24.Rmd-->




<!--chapter:end:topic_comments/topic25.Rmd-->




<!--chapter:end:topic_comments/topic26.Rmd-->




<!--chapter:end:topic_comments/topic27.Rmd-->




<!--chapter:end:topic_comments/topic28.Rmd-->

```{r t29a}
jjj <- 29
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t29b, fig.cap=paste0(fcap(the_categories$sub_lower[jjj]),"."),  fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t29c, fig.cap=paste(fcap(the_categories$sub_lower[jjj]), "articles in each journal."), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t29d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t29e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

In almost every model I ran, philosophy of religion was a single topic. But here, possibly because I was using so many topics, it split off ontological arguments from [the rest of philosophy of religion](#topic11). There are a few other articles in here on the general topic of arguments for God's existence, but they mostly are ontological argument papers. I didn't really realize that there were so many of them. There are, for example, about twice as many articles in the twelve journals on the ontological argument as on the Gettier problem, which is really not what I had realized.

<!--chapter:end:topic_comments/topic29.Rmd-->




<!--chapter:end:topic_comments/topic30.Rmd-->




<!--chapter:end:topic_comments/topic31.Rmd-->




<!--chapter:end:topic_comments/topic32.Rmd-->




<!--chapter:end:topic_comments/topic33.Rmd-->




<!--chapter:end:topic_comments/topic34.Rmd-->




<!--chapter:end:topic_comments/topic35.Rmd-->




<!--chapter:end:topic_comments/topic36.Rmd-->




<!--chapter:end:topic_comments/topic37.Rmd-->




<!--chapter:end:topic_comments/topic38.Rmd-->




<!--chapter:end:topic_comments/topic39.Rmd-->




<!--chapter:end:topic_comments/topic40.Rmd-->




<!--chapter:end:topic_comments/topic41.Rmd-->




<!--chapter:end:topic_comments/topic42.Rmd-->




<!--chapter:end:topic_comments/topic43.Rmd-->




<!--chapter:end:topic_comments/topic44.Rmd-->




<!--chapter:end:topic_comments/topic45.Rmd-->




<!--chapter:end:topic_comments/topic46.Rmd-->




<!--chapter:end:topic_comments/topic47.Rmd-->




<!--chapter:end:topic_comments/topic48.Rmd-->




<!--chapter:end:topic_comments/topic49.Rmd-->




<!--chapter:end:topic_comments/topic50.Rmd-->




<!--chapter:end:topic_comments/topic51.Rmd-->




<!--chapter:end:topic_comments/topic52.Rmd-->




<!--chapter:end:topic_comments/topic53.Rmd-->




<!--chapter:end:topic_comments/topic54.Rmd-->




<!--chapter:end:topic_comments/topic55.Rmd-->




<!--chapter:end:topic_comments/topic56.Rmd-->




<!--chapter:end:topic_comments/topic57.Rmd-->




<!--chapter:end:topic_comments/topic58.Rmd-->




<!--chapter:end:topic_comments/topic59.Rmd-->




<!--chapter:end:topic_comments/topic60.Rmd-->




<!--chapter:end:topic_comments/topic61.Rmd-->




<!--chapter:end:topic_comments/topic62.Rmd-->




<!--chapter:end:topic_comments/topic63.Rmd-->




<!--chapter:end:topic_comments/topic64.Rmd-->




<!--chapter:end:topic_comments/topic65.Rmd-->




<!--chapter:end:topic_comments/topic66.Rmd-->




<!--chapter:end:topic_comments/topic67.Rmd-->




<!--chapter:end:topic_comments/topic68.Rmd-->




<!--chapter:end:topic_comments/topic69.Rmd-->




<!--chapter:end:topic_comments/topic70.Rmd-->




<!--chapter:end:topic_comments/topic71.Rmd-->




<!--chapter:end:topic_comments/topic72.Rmd-->




<!--chapter:end:topic_comments/topic73.Rmd-->




<!--chapter:end:topic_comments/topic74.Rmd-->




<!--chapter:end:topic_comments/topic75.Rmd-->




<!--chapter:end:topic_comments/topic76.Rmd-->




<!--chapter:end:topic_comments/topic77.Rmd-->




<!--chapter:end:topic_comments/topic78.Rmd-->




<!--chapter:end:topic_comments/topic79.Rmd-->




<!--chapter:end:topic_comments/topic80.Rmd-->




<!--chapter:end:topic_comments/topic81.Rmd-->




<!--chapter:end:topic_comments/topic82.Rmd-->




<!--chapter:end:topic_comments/topic83.Rmd-->




<!--chapter:end:topic_comments/topic84.Rmd-->




<!--chapter:end:topic_comments/topic85.Rmd-->




<!--chapter:end:topic_comments/topic86.Rmd-->




<!--chapter:end:topic_comments/topic87.Rmd-->




<!--chapter:end:topic_comments/topic88.Rmd-->




<!--chapter:end:topic_comments/topic89.Rmd-->




<!--chapter:end:topic_comments/topic90.Rmd-->


# Summary Graphs {#summary-graphs}

Placeholder


## Main Summary Graph {#main-summary-graph}
## Graph Choices {#graph-choices}
## Raw Sum of Articles {#graph-rsa}
## Weighted Frequency of Articles {#graph-wfa}
## Raw Frequency of Articles {#graph-rfa}
## Weighted Sum of Pages {#graph-wsp}
## Raw Sum of Pages {#graph-rsp}
## Weighted Frequency of Pages {#graph-wfp}
## Raw Frequency of Pages {#graph-rfp}

<!--chapter:end:03-summary_graphs.Rmd-->


# Categories {#categorychapter}

Placeholder


## Graphs
## Split Topics
## Ethics {#ethics-category-section}
## History {#history-category-section}
## Logic and Mathematics
## Metaphysics {#metaphysics-category-section}
## Philosophy of Language
## Philosophy of Mind
## Philosophy of Science
## Social and Political

<!--chapter:end:04-categories.Rmd-->


# Sorting into Categories {#sortingchapter}

Placeholder


## Two Failed Attempts
## Splitting Up Topics {#subtopics-section}
## Summarising the Ninety Binary Sorts
## Classifying the One Hundred Topics and SubTopics
### Summary
## Idealism {#idealismsection}

<!--chapter:end:05-category_methodology.Rmd-->


# Epistemology {#epistemologychapter}

Placeholder



<!--chapter:end:06-epistemology.Rmd-->


# Eras and Decades {#eraschapter}

Placeholder


## Topics and Eras
## Categories and Eras
## Words and Eras {#words-eras}
## Topics and Decades
## Categories and Decades {#categories-decades}
## Words and Decades {#words-decades}

<!--chapter:end:07-eras.Rmd-->


# Outliers {#outliers}

Placeholder


## High-Confidence Articles {#high-confidence-articles}
## Low-Confidence Articles {#low-confidence-articles}
## High-Confidence Topics {#high-confidence-topics}
## Correlations {#correlation-section}
## Neighbors {#neighbours-section}
## Articles and Pages {#topic-length-section}
## Article Lengths {#article-length-section}
## The Bump {#the-bump}
## Trans-Atlantic Philosophy {#atlantic-section}
## Raw Counts and Weighted Counts {#raw-weight-count}

<!--chapter:end:08-outliers.Rmd-->


# Looking Outwards {#lookingoutward}

Placeholder


## Classic Books {#classic-book-section}
## Philosophers' Imprint {#imprint-section}
## Buzzwords {#buzzwords-section}

<!--chapter:end:09-buzzwords.Rmd-->


# References {-}

Placeholder


### Category Prevalence for Each Topic {-}
### Weighted Frequency of Categories in Each Year {-}
### Data Table for Figure 6.1 {-}
### Data Table for Figure 6.2 {-}
### Data Table for Figures 6.3 and 6.4 {-}
### Data Table for Figures 6.5 {-}

<!--chapter:end:references.Rmd-->

