# References {-}

Note that I'm not including here papers that are merely mentioned from the twelve journals, or from the other sources that were mined in chapter 9. But I am including papers where I drew on their content (beyond just their word distribution) in preparing this book.

<div id="refs"></div>

# (APPENDIX) Data Tables {-} 

# Subject Prominence by Subject

There are 90 tables below, one for each subject. In each table there are 138 rows, one for each year. In each year, there are 8 columns. This is what each of the columns represents.<br><br><br>

Weight
:    The weighted number of articles in that subject in that year. This is the main data point that's used throughout the book as the measure of the subject's prominence in the year.

Raw
:    The raw number of articles in that subject in that year.

W-Ratio
:    The weighted number of articles in that subject in that year per 1000 articles published that year.

R-Ratio
:    The raw number of articles in that subject in that year per 1000 articles published that year.

W-Pages
:    The weighted number of pages of articles on that subject in that year.

R-Pages
:    The raw number of pages of articles on that subject in that year.

WP-Ratio
:    The weighted number of pages of articles in that subject in that year per 1000 pages published that year.

RP-Ratio
:    The raw number of pages of articles in that subject in that year per 1000 pages published that year.


```{r append-two-loop}
app_a_table <- weight_numerator %>% 
  rename(Weight = y) %>% 
  mutate(Weight = round(Weight, 1)) %>% 
  full_join(count_numerator, by = c("year", "topic")) %>% 
  rename(Raw = y) %>% 
  full_join(weight_ratio, by = c("year", "topic")) %>%
  mutate(y = round(y * 1000)) %>% 
  rename(`W-Ratio` = y) %>% 
  select(-d) %>% 
  full_join(count_ratio, by = c("year", "topic")) %>%
  mutate(y = round(y * 1000)) %>% 
  rename(`R-Ratio` = y) %>% 
  select(-d) %>% 
  full_join(page_weight_numerator, by = c("year", "topic")) %>%
  mutate(y = round(y, 1)) %>% 
  rename(`W-Pages` = y) %>% 
  full_join(page_count_numerator, by = c("year", "topic")) %>%
  rename(`R-Pages` = y) %>% 
  full_join(page_weight_ratio, by = c("year", "topic")) %>%
  mutate(y = round(y * 1000)) %>% 
  rename(`WP-Ratio` = y) %>% 
  select(-d) %>% 
  full_join(page_count_ratio, by = c("year", "topic")) %>%
  mutate(y = round(y * 1000)) %>% 
  rename(`RP-Ratio` = y) %>% 
  select(-d) %>% 
  rename(Year = year)
  
  
for (jjj in 1:90){
  cat_subject <- the_categories$subject[jjj]

  cat(" \n")
  cat("### ", cat_subject, " {-#a",jjj,"}\n\n", sep="")

  temp <- filter(app_a_table, topic == jjj) %>% 
    arrange(Year) 
  
  print(
    kable(
      temp %>% select(-topic), 
      label = paste0("appendyearfre",jjj),
      caption = paste("Measures of the prominence of", cat_subject, "in each year's journals.")) 
  )
}
```

# Subject Prominence by Year

There are 138 tables below, one for each year In each table there are 90 rows, one for each subject. In each row, there are 8 columns. This is what each of the columns represents.<br><br><br>

Weight
:    The weighted number of articles in that subject in that year. This is the main data point that's used throughout the book as the measure of the subject's prominence in the year.

Raw
:    The raw number of articles in that subject in that year.

W-Ratio
:    The weighted number of articles in that subject in that year per 1000 articles published that year.

R-Ratio
:    The raw number of articles in that subject in that year per 1000 articles published that year.

W-Pages
:    The weighted number of pages of articles on that subject in that year.

R-Pages
:    The raw number of pages of articles on that subject in that year.

WP-Ratio
:    The weighted number of pages of articles in that subject in that year per 1000 pages published that year.

RP-Ratio
:    The raw number of pages of articles in that subject in that year per 1000 pages published that year.


```{r append-three-loop}
app_b_table <- weight_numerator %>% 
  rename(Weight = y) %>% 
  mutate(Weight = round(Weight, 1)) %>% 
  full_join(count_numerator, by = c("year", "topic")) %>% 
  rename(Raw = y) %>% 
  full_join(weight_ratio, by = c("year", "topic")) %>%
  mutate(y = round(y * 1000)) %>% 
  rename(`W-Ratio` = y) %>% 
  select(-d) %>% 
  full_join(count_ratio, by = c("year", "topic")) %>%
  mutate(y = round(y * 1000)) %>% 
  rename(`R-Ratio` = y) %>% 
  select(-d) %>% 
  full_join(page_weight_numerator, by = c("year", "topic")) %>%
  mutate(y = round(y, 1)) %>% 
  rename(`W-Pages` = y) %>% 
  full_join(page_count_numerator, by = c("year", "topic")) %>%
  rename(`R-Pages` = y) %>% 
  full_join(page_weight_ratio, by = c("year", "topic")) %>%
  mutate(y = round(y * 1000)) %>% 
  rename(`WP-Ratio` = y) %>% 
  select(-d) %>% 
  full_join(page_count_ratio, by = c("year", "topic")) %>%
  mutate(y = round(y * 1000)) %>% 
  rename(`RP-Ratio` = y) %>% 
  select(-d) %>% 
  mutate(topic = as.numeric(topic)) %>% 
  left_join(the_categories, by = "topic") %>% 
  arrange(year, topic) %>% 
  select(-cat_num, -cat_name, -topic) %>% 
  select(Subject = subject, everything())
  
  
  
for (jjj in 1:138){
  cat_subject <- jjj + 1875

  cat(" \n")
  cat("### ", cat_subject, " {-#b",jjj,"}\n\n", sep="")

  temp <- filter(app_b_table, year == cat_subject)
  
  print(
    kable(
      temp %>% select(-year), 
      label = paste0("appendsubjectfre",cat_subject),
      caption = paste("Measures of the prominence of each subject in ", cat_subject, "'s journals.")) 
  )
}
```

# Data Tables for Chapter 4

### Category Prevalence for Each Topic {-}

```{r category-count-table}

temp <- category_count %>% 
  arrange(year, category) %>% 
  full_join(category_year, by  = c("year", "category")) %>% 
  mutate(y = round(y * 10)/10) %>% 
  full_join(category_frequency %>% 
              arrange(year, category) %>%
              select(year, category, f), by = c("year", "category")) %>% 
  mutate(f = scales::percent(f, accuracy = 0.1, suffix = "%")) %>% 
  select(category, Year = year, Count = n, `Weighted Count` = y, `Weighted Frequency` = f)

cat_list <- temp %>% 
  ungroup() %>% 
  group_by(category) %>% 
  tally()

for (jjj in cat_list$category){
  temp2 <- temp %>% 
    filter(category == jjj) %>% 
    select(-category)
  
cat("**",jjj,"**  \n  \n", sep="")

print(
  kable(
    temp2, align = 'lccc', caption = paste0("Three measures of the prevalence of ",jjj," in each year.")
  )
)
}
```

### Weighted Frequency of Categories in Each Year {-}

```{r category-by-year}
temp <- category_frequency %>% 
  select(year, category, f) %>% 
  mutate(f = scales::percent(f, accuracy = 0.1, suffix = "%")) %>% 
  pivot_wider(id_cols = year, names_from = category, values_from = f) %>% 
  rename(Year = year)

temp1 <- temp %>% 
  select(c(1, 4, 5, 7, 10, 12, 13))

temp2 <- temp %>% 
  select(c(1, 2, 3, 6, 8, 9, 11))
  
kable(temp1, align = c('r', 'c', 'c', 'c', 'c', 'c', 'c'), caption = "Weighted frequency by year for six larger topics.")

kable(temp2, align = c('r', 'c', 'c', 'c', 'c', 'c', 'c'), caption = "Weighted frequency by year for six smaller topics.")
```


<!-- ### Data Table for Figures 4.1 and 4.2 {-} -->

<!-- ```{r category-count-table} -->
<!-- temp <- category_count %>%  -->
<!--   arrange(year, category) %>%  -->
<!--   rename(Year = year, Category = category, `Number of Articles` = n) -->

<!-- kable(temp, caption = "Number of articles in each category in each year.") -->
<!-- ``` -->

<!-- ### Data Table for Figures 4.3 and 4.4 {-} -->

<!-- ```{r category-weight-table} -->
<!-- temp <- category_year %>%  -->
<!--   arrange(year, category) %>% -->
<!--   mutate(y = round(y * 10)/10) %>%  -->
<!--   rename(Year = year, Category = category, `Weighted Number of Articles` = y) -->

<!-- kable(temp, caption = "Weighted number of articles in each category in each year.") -->
<!-- ``` -->

<!-- ### Data Table for Figures 4.5 and 4.6 {-} -->

<!-- ```{r category-weighted-frequency-table} -->
<!-- temp <- category_frequency %>%  -->
<!--   arrange(year, category) %>% -->
<!--   select(year, category, f) %>%  -->
<!--   mutate(f = scales::percent(f, accuracy = 0.1, suffix = "%")) %>%  -->
<!--   rename(Year = year, Category = category, `Weighted Frequency of Articles` = f) -->

<!-- kable(temp, caption = "Weighted frequency of articles in each category in each year.") -->
<!-- ``` -->

<!-- ### Data Table for Figure 4.7 {-} -->

<!-- ```{r category-frequency-facet} -->
<!-- temp <- category_frequency %>%  -->
<!--   arrange(category, year) %>% -->
<!--   select(category, year, f) %>%  -->
<!--   mutate(f = scales::percent(f, accuracy = 0.1, suffix = "%")) %>%  -->
<!--   rename(Year = year, Category = category, `Weighted Frequency of Articles` = f) -->

<!-- kable(temp, caption = "Weighted frequency of articles in each year for each category.") -->
<!-- ``` -->

# Data Tables for Chapter 6

### Data Table for Figure 6.1 {-}

```{r epistemology-summary-table}
temp <- epistemology_yearcount %>% 
  arrange(year) %>% 
  select(year, n) %>% 
  rename(Year = year, `Number of Articles` = n)

kable(temp, align = 'cc', caption = "Number of Epistemology articles in each year.")
```

### Data Table for Figure 6.2 {-}


```{r epistemology-topic-count}
temp <- epistemology_yeartopics_postwar %>% 
  drop_na() %>% 
  arrange(year, topic) %>% 
  select(year, topic, tn) %>% 
  filter(topic <= 10) %>% 
  pivot_wider(id_cols = year, names_from = topic, values_from = tn) %>% 
  rename(Year = year)

kable(temp, align = 'rcccccccccc', caption = "Raw number of Epistemology articles in topics 1-10 in each year.")

temp <- epistemology_yeartopics_postwar %>% 
  drop_na() %>% 
  arrange(year, topic) %>% 
  select(year, topic, tn) %>% 
  filter(topic > 10, topic <= 20) %>% 
  pivot_wider(id_cols = year, names_from = topic, values_from = tn)  %>% 
  rename(Year = year)

kable(temp, align = 'rcccccccccc', caption = "Raw number of Epistemology articles in topics 11-20 in each year.")

temp <- epistemology_yeartopics_postwar %>% 
  drop_na() %>% 
  arrange(year, topic) %>% 
  select(year, topic, tn) %>% 
  filter(topic > 20, topic <= 30) %>% 
  pivot_wider(id_cols = year, names_from = topic, values_from = tn)  %>% 
  rename(Year = year)

kable(temp, align = 'rcccccccccc', caption = "Raw number of Epistemology articles in topics 21-30 in each year.")

temp <- epistemology_yeartopics_postwar %>% 
  drop_na() %>% 
  arrange(year, topic) %>% 
  select(year, topic, tn) %>% 
  filter(topic > 30, topic <= 40) %>% 
  pivot_wider(id_cols = year, names_from = topic, values_from = tn)  %>% 
  rename(Year = year)

kable(temp, align = 'rcccccccccc', caption = "Raw number of Epistemology articles in topics 31-40 in each year.")



```

### Data Table for Figures 6.3 and 6.4 {-}


```{r epistemology-topics-weight}
temp <- epistemology_yeargamma_postwar %>% 
  drop_na() %>% 
  arrange(year, topic) %>% 
  select(year, topic, gamsum) %>% 
  filter(topic <= 10) %>% 
  mutate(gamsum = round(gamsum, 1)) %>% 
  pivot_wider(id_cols = year, names_from = topic, values_from = gamsum) %>% 
  rename(Year = year)

kable(temp, align = 'rcccccccccc', caption = "Weighted number of Epistemology articles in topics 1-10 in each year.")

temp <- epistemology_yeargamma_postwar %>% 
  drop_na() %>% 
  arrange(year, topic) %>% 
  select(year, topic, gamsum) %>% 
  filter(topic > 10, topic <= 20) %>% 
  mutate(gamsum = round(gamsum, 1)) %>% 
  pivot_wider(id_cols = year, names_from = topic, values_from = gamsum)  %>% 
  rename(Year = year)

kable(temp, align = 'rcccccccccc', caption = "Weighted number of Epistemology articles in topics 11-20 in each year.")

temp <- epistemology_yeargamma_postwar %>% 
  drop_na() %>% 
  arrange(year, topic) %>% 
  select(year, topic, gamsum) %>% 
  filter(topic > 20, topic <= 30) %>% 
  mutate(gamsum = round(gamsum, 1)) %>% 
  pivot_wider(id_cols = year, names_from = topic, values_from = gamsum)  %>% 
  rename(Year = year)

kable(temp, align = 'rcccccccccc', caption = "Weighted number of Epistemology articles in topics 21-30 in each year.")

temp <- epistemology_yeargamma_postwar %>% 
  drop_na() %>% 
  arrange(year, topic) %>% 
  select(year, topic, gamsum) %>% 
  filter(topic > 30, topic <= 40) %>% 
  mutate(gamsum = round(gamsum, 1)) %>% 
  pivot_wider(id_cols = year, names_from = topic, values_from = gamsum)  %>% 
  rename(Year = year)

kable(temp, align = 'rcccccccccc', caption = "Weighted number of Epistemology articles in topics 31-40 in each year.")


```

### Data Table for Figures 6.5 {-}


```{r epistemology-categories-count}
temp <- epistemology_categories %>% 
  arrange(year, category) %>% 
  select(year, category, y) %>% 
  mutate(y = round(y, 1)) %>% 
  pivot_wider(id_cols = year, names_from = category, values_from = y) %>% 
  rename(Year = year)

kable(temp, align = 'rccccc', caption = "Weighted number of Epistemology articles in each category in each year.")
```
