```{r t20a}
jjj <- 20
source('topic_summary_data.R')
opts_knit$set(eval.after = "fig.cap")
```

```{r t20b, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal")}
source('topic_summary_facet_graph.R')
```

```{r t20c, fig.cap=the_categories$subject[jjj], fig.height= 5.2}
cat("<br>")
source('topic_summary_overall_graph.R')
```

```{r t20d}
cat("<br>")
source('topic_summary_char_art.R')
temp_dt
```

```{r t20e}
cat("<br>")
source('topic_summary_high_cites.R')
if(is_high_cites == 1)
	{cat("<br>")}
if(is_high_cites == 1)
	{high_table}
if(is_high_cites == 1)
	{cat("<br>")}
cat("\n
	**Comments**
	\n")
```

This topic contains a bunch of stuff on space and time in classical
(i.e., pre-relativistic) physics, some stuff on philosophical issues
arising in geometry, and some historical work connected to those two
things. It has a lot of overlap with [Topic 50](#topic50) The big
differences are that this topic is more classical, and topic 50 is
more relativistic. And topic 50 is considerably more technical and
mathemtical. I've used the first difference to name the topics, but
the second difference is what made this go in metaphysics, while topic
50 goes in philosophy of science.

The characteristic articles in this case are somewhat
uncharacteristic. The bulk of the articles in the topic are simply
about space and time. But those articles are the ones that the model
was most hesitant about clearly putting in this topic rather than 50,
and so they don't have the highest probability of being in the topic.
The articles about geometry, and about Reid, didn't confuse the model
as much, so they get listed here.

Other model runs didn't distinguish classical from relativistic work
on space time. They would routinely distinguish work on quantum
mechanics from classical and relativistic mechanics, but the classical
versus relativistic distinction was a bit rarer. What sometimes did
get included in place of this topic was a topic centered on workabout
philosophy of geometry and measurement. That's still a small topic,
but quite a lively one. [Brent
Mundy](https://philpapers.org/s/brent%20mundy) did a lot of important
work in this field, and recently there has been important work by [Tim
Maudlin](https://philpeople.org/profiles/tim-maudlin) and by [Cian
Dorr](https://philpeople.org/profiles/cian-dorr). In other model runs
this work was classified together with the Reid-influenced work on
geometry, and that was arguably a better classification.