```{r t27a}
jjj <- 27
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t27b, fig.cap=the_categories$subject[jjj], fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t27c, fig.cap=paste(the_categories$subject[jjj], "articles in each journal."), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t27d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t27e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

In earlier iterations of this project I ran through a few different journals. And one of the effects of doing this was that I'd occasionally see topics that weren't really that big in philosophy in general, but were a big deal in that journal. And some of them were very distinctive to the interests of one or other journal editor. This iteration of the project mostly didn't have this; very few topics are held up by a single journal.

This topic is an exception. The graph for _Philosophy and Phenomenological Research_ obviously looks very different to the graphs for the rest of the journals. But I don't think this means that that we're seeing something unrepresentative here. Rather, what we're seeing is something like a blindspot (or deliberate oversight) in the other eleven journals which is counter-balanced by _Philosophy and Phenomenological Research_. This does mean that when PPR changes its focus in the 1980s, this topic seems to fall away very quickly. That's misleading though, if one cares about all of philosophy. What's really true is that the topic moves away from these twelve journals, and this becomes a respect in which the twelve journals are less than fully representative of philosophy.

I'm calling this a history topic because most of the papers feel historical; they are looking back at work done in the glory days of phenomenology. But those 1940s papers that make up a chunk of the topics weren't intended as being papers in history of philosophy; they were just doing philosophy. This is a systematic challenge with a study this long. If I extended the study even further - say by putting include 17th to 19th century books - we'd see even more dramatic versions of this effect. Topic modeling can't typically tell works by an author apart from works about that author, so any historical figure will be grouped in with the history of work on that author.