```{r t80a}
jjj <- 80
source('topic_summary_data.R')
opts_knit$set(eval.after = "fig.cap")
```

```{r t80b, fig.cap=the_categories$subject[jjj], fig.height= 5.2}
source('topic_summary_overall_graph.R')
```

```{r t80c, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal")}
cat("<br>")
source('topic_summary_facet_graph.R')
```

```{r t80d}
cat("<br>")
source('topic_summary_char_art.R')
temp_dt
```

```{r t80e}
cat("<br>")
source('topic_summary_high_cites.R')
if(is_high_cites == 1)
	{cat("<br>")}
if(is_high_cites == 1)
	{high_table}
if(is_high_cites == 1)
	{cat("<br>")}
cat("\n
	**Comments**
	\n")
```

Lots of ways to carve up metaphysics. This model puts possible worlds together with dispositions. That sort of makes sense. But it's a little weird - both topics are more connected to counterfactuals than they are to each other. Yet counterfactuals aren't in here. Oh well. And you could put either in with laws, but they aren't really in here either. 

Would have loved to have included AJP in this, and then we really would have had a Lewis centric topic. As it is, Lewis is a keyword in this, and turns up in the citations (i.e., as author or as named in the title) in 21 articles in this topic. The word 'Lewis' turns up in three others, but it's C. I. Lewis not David.