```{r t26a}
jjj <- 26
source('topic_summary_data.R')
opts_knit$set(eval.after = "fig.cap")
```

```{r t26b, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal")}
source('topic_summary_facet_graph.R')
```

```{r t26c, fig.cap=the_categories$subject[jjj], fig.height= 5.2}
cat("<br>")
source('topic_summary_overall_graph.R')
```

```{r t26d}
cat("<br>")
source('topic_summary_char_art.R')
temp_dt
```

```{r t26e}
cat("<br>")
source('topic_summary_high_cites.R')
if(is_high_cites == 1)
	{cat("<br>")}
if(is_high_cites == 1)
	{high_table}
if(is_high_cites == 1)
	{cat("<br>")}
cat("\n
	**Comments**
	\n")
```

A more accurate, if less pithy, name for this category would be _Mid-Century General Philosophy of Science_. It isn't all mid-century; if you scroll down the list of articles in the topic you see several from recent years. But there is something mid-century about the spirit of it; it's philosophy of science that is very much not philosophy of one or other science in particular. And as that has gone out of fashion, this topic has declined.

The statistics for this topic were very surprising. The years make sense; mid-century philosophy peaks in the mid-century. But the numbers show how misleading the graphs can be. Eyeballing the graphs makes it look like this was just bubbling along; but the numbers say it is the 5th or 6th biggest topic of the 90. The story here, I think, is that there was much less specialisation in the 1950s and 1960s, and so individual topics get a chance to grow a lot.

And the topic overlaps were surprising enough to make me recheck the code. It isn't completely surprising that philosophy of science would intersect somewhat with Marx. "Scientific Socialism" was a thing, and plenty of philosophers of science had Marxist sympathies. And there is a lot of time sensitivity to these analyses, and Marx was a big topic at the same time that this topic was bit. But that it would be the highest overlap was a surprise. And it shows you how much philosophy of science has changed that Formal Epistemology is literally the lowest overlap.