```{r t09a}
jjj <- 9
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t09b, fig.cap=the_categories$subject[jjj], fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t09c, fig.cap=paste(the_categories$subject[jjj], "articles in each journal."), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R') # Burp
```

```{r t09d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic # Burp
temp_dt
```

```{r t09e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

I really didn't expect this. I sort of thought that physicalism, in the way it was discussed by contemporary writers, was quite distinct from what early twentieth century writers were talking about. And I thought that even if that weren't true, the terminological changes - using language like 'supervenience' and 'physicalism' that I thought was not common in the early twentieth century - would have been enough to get the model to split up Stoljar and Montero from Stebbing and Trumbull Ladd. But the model thinks that they fit together, and I can sort of see it's point of view.

The mind-body problem is one of the oldest and most venerable problems around. Actually, since we're discussing Stoljar, I should at this point acknowledge [his good point](http://dailynous.com/2017/11/07/philosophy-makes-progress-guest-post-daniel-stoljar/) that it is a class of problems not a problem, and missing this point leads one to seriously misstate the history of work in this field [@Stoljar2017]. It was a big deal in nineteenth century philosophy, it is a big deal in twenty-first century philosophy, and, apparently, it was an even bigger deal in philosophy in the 1920s and 1930s.

The only thing that disappoints me about the model's result here is that it put almost none of Samuel Alexander's work in this topic. I'd have thought the pre-eminent emergentist of the early twentieth century would play an important role in debates about physicalism, but the model disagreed, and I'm not entirely sure why it did so.