```{r t58a}
jjj <- 58
source('topic_comments/topic_summary_data.R') # Get data
opts_knit$set(eval.after = "fig.cap")
```

```{r t58b, fig.cap=the_categories$subject[jjj], fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t58c, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal")}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t58d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t58e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

This is another topic that came in a little smaller than I expected, perhaps in part because the model was construing it slightly more narrowly than I was. I certainly would have guessed that articles about Minds and Machines would be much more than 0.6-0.8% of the articles.

The explanation here is that the topic got squeezed from all sides. There are topics about [Physicalism](#topic09), [Conceivability Arguments](#topic55), [Wide Content](#topic85) and [Cognitive Science](#topic87). What's left here are articles on a very specific range of arguments about whether minds are best thought of as machines. Put that way, the real surprise is that it hasn't faded more. You can see a small downward trajectory towards the right-hand edge, but only a small one. Issues that Turing, Godel, Searle and others raised continue to fascinate philosophers.