```{r t39a}
jjj <- 39
source('topic_summary_data.R')
opts_knit$set(eval.after = "fig.cap")
```

```{r t39b, fig.cap=paste(the_categories$subject[jjj], fig.height= 5.2}
source('topic_summary_overall_graph.R')
```

```{r t39c, fig.cap=the_categories$subject[jjj], "Articles in Each Journal")}
cat("<br>")
source('topic_summary_facet_graph.R')
```

```{r t39d}
cat("<br>")
source('topic_summary_char_art.R')
temp_dt
```

```{r t39e}
cat("<br>")
source('topic_summary_high_cites.R')
if(is_high_cites == 1)
	{cat("<br>")}
if(is_high_cites == 1)
	{high_table}
if(is_high_cites == 1)
	{cat("<br>")}
cat("\n
	**Comments**
	\n")
```

One of four different topics the model found on time, which has been a continuing source of interest in the journals. This one is on broadly speaking the existence of times. We've already looked discussions of the [temporal paradoxes](#topic19), and [space and time in classical physics](#topic20). and we're coming up to the discussion of [space and time in relativistic physics](#topic50). And that's setting aside the [Composition and Constitution](#topic89), which includes a lot of papers on temporal parts.

Especially compared to its neighbours in debates about time, this one has a very flat distribution across time. Perhaps there is some kind of irony in this. We can see this if we look at all four topics on a single graph. (I'm starting this in the 20th century to exclude some outlier years, and included trend lines to make things clearer.)

```{r graph-time-categories, fig.cap = "Time topics - Weighted Frequency of Articles"}
  weight_ratio_graph <- ggplot(filter(weight_ratio, topic == 19 | topic == 20 | topic == 39 | topic == 50), aes(x = year, y = y, color=topic, group=topic))
  weight_ratio_graph + 
    coord_cartesian(xlim = c(1900, 2013), ylim = c(0, 0.04)) +
    scale_colour_discrete(labels = c(the_categories$subject[19], the_categories$subject[20], the_categories$subject[39], the_categories$subject[50])) + 
    theme(legend.title = element_blank(), legend.position = "bottom") +
    geom_point(size = 1, alpha = .5) +
    geom_smooth(se = F, method = "loess", size = .5, formula = "y ~ x") +
    labs(x = "Year", y = "Weighted Frequency of Articles")
```

The two early topics gradually fall, though maybe they have both reached a steady state. Relativistic space and time rises through around 1980, though it too might have obtained an equilibrium. But this topic, the metaphysics of time(s) stays at a very steady level around 1% year after year.
