```{r t84a}
jjj <- 84
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t84b, fig.cap=the_categories$subject[jjj], fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t84c, fig.cap=paste(the_categories$subject[jjj], "articles in each journal."), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t84d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t84e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

When I was a graduate student, this was the stuff I worked on - indicative conditionals and probabilistic models of rational agents. At the time, I thought of myself as working at the intersection of philosophy of science and philosophy of language. It was only when I started applying for jobs that I thought, well, since what I'm doing is working on stuff about rationality, maybe I should just insist that it counts as epistemology and see if I get away with it. Twenty-something years later, no one in my position has such worries; this is clearly part of epistemology.

One way to see how much it has changed is to look at where the papers are being published. Here's a version of the facet graph above but restricted to the period since 1980, and with trendlines added.

```{r formal-epistemology-journal-distribution, fig.cap = "Recent Formal Epistemology", fig.alt = alt_text}
facet_labels <- chap_two_facet_labels %>%
  mutate(year = 1983, gamfre = yupper)

facet_labels$journal <- factor(facet_labels$journal, levels = journal_order)

indiv_journal_graphs +
  coord_cartesian(xlim = c(1980,2013)) +
  geom_smooth(method = "loess", formula = "y ~ x", se = F, size = 0.1) +
  geom_text(data = facet_labels,
            mapping = aes(label = short_name),
            vjust = "inward", 
            hjust = "inward",
            fontface = "bold", 
            size = 3,
            colour = "grey40")

alt_text <- "A version of figure 2.188 restricted to the years from 1980-2013. The data shows that this topic stayed relatively flat in 9 journals, but took off in Mind, Philosophical Review, and Noûs."
```

I think this makes clear something that was intuitively plausible: that it's the generalist journals leading the charge here. As work on Bayesianism has moved from being Philosophy of Science to Epistemology, it has become a much bigger part of what _Mind_, _Philosophical Review_ and _Noûs_ have published. (Though, to be sure, a lot of what's happened in _Noûs_ has been since 2013.) I'm a little surprised there isn't more movement on the _Analysis_ grap; I would have guessed the Sleeping Beauty debate alone would have pushed it higher. But otherwise this looks like a case where the general picture - that this went from something of a specialist topic to a 'generalist' one - is borne out by the data.