```{r t64a}
jjj <- 64
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t64b, fig.cap=paste0(fcap(the_categories$sub_lower[jjj]),"."),  fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t64c, fig.cap=paste(fcap(the_categories$sub_lower[jjj]), "articles in each journal."), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t64d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t64e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

The model is carving things up a little more finely than may be ideal here, so let's put some stuff back together. This topic obviously has a lot to do with [denoting](#topic43) and with [belief ascriptions](#topic72). And it's useful to see all three of these on a single graph.

```{r three-language-topics, fig.height = 5, fig.cap= "Relative frequency of denoting, sense and reference, and belief ascriptions", fig.alt = alt_text}
frb <- weight_ratio %>%
  filter(topic == 43 | topic == 64 | topic == 72) 

ggplot(frb, mapping = aes(x = year, y = y, color = topic)) + 
  spaghettistyle +
  geom_point(alpha = 0.5) + 
  geom_smooth(se = F, size = 0.5, method = "loess", formula = "y ~ x") +
  labs(x = element_blank(), y = "Weighted proportion of articles", title = "Three Classic Topics") +
  scale_color_discrete(name = "Topics", labels = c("Denoting", "Sense and reference", "Belief ascriptions"))

alt_text <- "The graphs for three topics—denoting, sense and reference, and belief ascriptions—on one chart. The shape of the graph is described in the text below."
```

There is a tiny amount of discussion of these three, mostly focussed on descriptions, up until World War II. Then they all start to take off. But descriptions as such starts to fade quite early, with its peak being the late 1970s. Some of that is just substitution—there is a lot of discussion of how descriptions work in articles on sense and reference, and articles on belief ascriptions. But the sum seems to be headed a little downwards as we move into the twenty-first century, and I'd expect that gentle trend continues through 2020.

Even at their peak, these topics don't take up as much space in the journals as they take up in philosophers' self-representation. At most these topics are coming to about 3–4 ercent of the discussion over any sustained period of time. But during that time they were routinely taking up more than 3—4 percent of space in graduate education. (For instance, it was not unusual to have compulsory first-year seminars largely about these topics.) My feeling is that the journals got this right and the departments got this wrong, and 3–4 percent was a sensible proportion of space to devote to these topics. That said, it was surprising to me that this never went much higher than that; it certainly felt at times like more than 3–4 percent of the discussion was devoted to denotation, sense, reference and opaque contexts.