```{r t78a}
jjj <- 78
source('topic_comments/topic_summary_data.R') # Get data
opts_knit$set(eval.after = "fig.cap")
```

```{r t78b, fig.cap=the_categories$subject[jjj], fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t78c, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal")}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t78d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t78e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

Given the importance of Concepts to late twentieth century philosophy, this is a surprisingly small topic. I think that what's happened here is that it has just gotten squeezed by other topics. There isn't a single article that's more than 10 pages long with a probability of being in this topic of over 0.5.

Part of the story about this topic is similar to the story with the topic on [Arguments](#topic55). More philosophers write about concepts in papers on other topics than write papers directly about concepts. This isn't surprising, but it did surprise me a bit that there aren't more papers directly about concepts in the journals. There are several important books on concepts, and there are papers in specialist journals like _Mind and Language_, and that led me to expect that there would be more here than turned out to be the case.