```{r t80a}
jjj <- 80
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t80b, fig.cap=the_categories$subject[jjj], fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t80c, fig.cap=paste(the_categories$subject[jjj], "articles in each journal."), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t80d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t80e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

The top graph makes it look like this is a story of more or less continuous growth from the early 1960s onwards. But under the surface the story is a little more complicated. The topic includes articles about the nature of modality, and in particular the nature of possible worlds, but also articles about the nature of dispositions. 

There are a lot of ways to carve up metaphysics into topics. This one makes some sense, but is also a bit puzzling. Both work on modality and work on dispositions are more connected to work on counterfactual conditionals than they are to each other. The end result is convenient for my project; I get two debates that are both in metaphysics, and reasonably close to each other, in the one topic. It's just funny to see them both separated from counterfactuals in this way.

David Lewis is as important to the journals from 1965 onward as any other philosopher, but he doesn't have any one topic that is really centered around his work. This is as close as it gets. Twenty-one of the articles here are either by Lewis, or reference him in their title. (There are other articles with "Lewis" in the title, but they are about C. I. Lewis, not David Lewis.) My biggest regret of this project was that I couldn't include the _Australasian Journal of Philosophy_ because it wasn't in the JSTOR database. That would have given a much better sense of how Lewis's papers related to the general themes of the era.