```{r t10a}
jjj <- 10
source('topic_summary_data.R')
opts_knit$set(eval.after = "fig.cap")
```

```{r t10b, fig.cap=paste(the_categories$subject[jjj], fig.height= 5.2}
source('topic_summary_overall_graph.R')
```

```{r t10c, fig.cap=the_categories$subject[jjj], "Articles in Each Journal")}
cat("<br>")
source('topic_summary_facet_graph.R')
```

```{r t10d}
cat("<br>")
source('topic_summary_char_art.R')
temp_dt
```

```{r t10e}
cat("<br>")
source('topic_summary_high_cites.R')
if(is_high_cites == 1)
	{cat("<br>")}
if(is_high_cites == 1)
	{high_table}
if(is_high_cites == 1)
	{cat("<br>")}
cat("\n
	**Comments**
	\n")
```

This is a topic that I find quite interesting, but which has largely vanished from contemporary philosophy. It's largely philosophy of history, with quite a bit of attention paid to Collingwood and Toynbee. But there is also work at the intersection between philosophy and sociology, and more generally work discussing culture. There is a smattering of work here that we'd call history of philosophy, such as the paper you see above on Vico, but there is much more work about history the discipline than history of philosophy.

There are also a handful of papers on the philosophical significance of various political figures, such as Jefferson, Lenin or Roosevelt. Analytical political philosophy has something of an aversion to dealing with figures who were politically influential in their own time. Even when we do study such figures, we tend to steer away from the works that actually made them influential. There are ongoing attempts to make Anglophone political philosophers take Ghandi and Martin Luther King Jr. more seriously. If those attempts succeed, they will not just increase the racial diversity of who gets studied, but also introduce figures who were seriously influential in their own lifetme.