```{r t38a}
jjj <- 38
source('topic_comments/topic_summary_data.R') # Get data
opts_knit$set(eval.after = "fig.cap")
```

```{r t38b, fig.cap=the_categories$subject[jjj], fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t38c, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal")}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t38d}
source('topic_comments/topic_summary_char_art.R')
temp_dt
```

```{r t38e}
source('topic_comments/topic_summary_high_cites.R')
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n
	**Comments**
	\n")
```

A tiny topic, but still one that seemed to need breaking up in order to categorise. The papers are mostly about origins and ends, which make sense as a unified category. But then it bifurcates into debates within metaphysics, primarily about essentialism and identity over time, and in philosophy of science, about the role of teleological reasoning. 

There are only 90 articles here, so there isn't a ton to say about them collectively. It was a little surprising to me that we don't see a Kripke/Parfit related bump in the 1970s for work on personal identity, especially since so much of the work is on origin essentialism. Part of the story is that there is a bit of work in the British journals on personal identity before the Kripke/Parfit boom, some of it inspired by Wiggins. And the topic is small enough that that's enough to stop there being a huge rise once Kripkean and Parfittian theories of personal identity become prominent.
