```{r t83a}
jjj <- 83
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t83b, fig.cap=paste0(fcap(the_categories$sub_lower[jjj]),"."),  fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t83c, fig.cap=paste(fcap(the_categories$sub_lower[jjj]), "articles in each journal."), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t83d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t83e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

I've called this population ethics, but it's really contemporary utilitarianism. For various reasons the term _consequentialism_ became more popular over this time period, and the model doesn't really know that this is a near synonym for 'utilitarianism', so it puts the consequentialist articles and the utilitarian articles in separate categories. I didn't feel like naming the topic after what is something of a terminological change. I could have called it numbers and ethics, which would have been accurate enough if a little frivolous. Instead, I focused on Parfit's centrality to the topic and called it population ethics.

It's mildly surprising to me that "[Famine, Affluence and Morality](https://philpapers.org/rec/SINFAA)" is in here. Of course, it is a consequentialist article. But most of this topic lives at a much higher level of abstraction. Partially what happened was that the model I'm using didn't really settle on a single applied ethics topics. Other runs of the model had topics where "[Famine, Affluence and Morality](https://philpapers.org/rec/SINFAA)" and "[A Defense of Abortion](https://philpapers.org/rec/THOADO-2)" as twin pillars of a big applied ethics topic. But here they got split, and so Singer's paper ends up with quite a bit of high theory around it.

And I know I'm being repetitive on this, but it's just shocking to me to see how little of this work is turning up in the "generalist" journals. The left-two columns in the graph suggest this was an incredibly niche, minor part of contemporary philosophy, with perhaps a small bubble of interest in the 1990s and early 2000s that had faded. And that would be completely the wrong picture. That's why I felt it was essential to include the "specialist" journals in this study; it's not possible to get an accurate picture of the discipline without them.