```{r t42a}
jjj <- 42
source('topic_summary_data.R')
opts_knit$set(eval.after = "fig.cap")
```

```{r t42b, fig.cap=paste(the_categories$subject[jjj], fig.height= 5.2}
source('topic_summary_overall_graph.R')
```

```{r t42c, fig.cap=the_categories$subject[jjj], "Articles in Each Journal")}
cat("<br>")
source('topic_summary_facet_graph.R')
```

```{r t42d}
cat("<br>")
source('topic_summary_char_art.R')
temp_dt
```

```{r t42e}
cat("<br>")
source('topic_summary_high_cites.R')
if(is_high_cites == 1)
	{cat("<br>")}
if(is_high_cites == 1)
	{high_table}
if(is_high_cites == 1)
	{cat("<br>")}
cat("\n
	**Comments**
	\n")
```

This is a bit of a grab-bag of papers, loosely connected to the idea of depiction. I've classified it as Aesthetics because it includes papers like

- [Analysis of the Poetic Similie](https://philpapers.org/rec/RIEAOT) by Max Reiser.
- [On What A Painting Represents](https://philpapers.org/rec/ZIFOWA) by Paul Ziff.
- [The Aesthetics Of Photographic Transparency](https://philpapers.org/rec/LOPTAO) by Dominic MacIver Lopes.

But it also includes papers that seem less neatly classed as Aesthetics, like

- [You Can Call Me 'Stupid', ... Just Don't Call Me Stupid](https://philpapers.org/rec/FARYCC) by Delia Graff Fara.
- [Self To Self](https://philpapers.org/rec/VELSTS) by David Velleman.
- [On the New Riddle of Induction](https://philpapers.org/rec/BAROTN-2) by S. F. Barker and Peter Achinstein.

Still, the aesthetics papers predominate, so that's the category I've gone with. Very often these models would locate the Aesthetics papers quite neatly and put them in a category. But this model has separated out these papers on depiction from the larger category of papers on beauty. And the result is that the topic is fairly small.