```{r t67a}
jjj <- 67
source('topic_comments/topic_summary_data.R') # Get data
opts_knit$set(eval.after = "fig.cap")
```

```{r t67b, fig.cap=the_categories$subject[jjj], fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t67c, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal")}

source('topic_comments/topic_summary_facet_graph.R')
```

```{r t67d}

source('topic_comments/topic_summary_char_art.R')
temp_dt
```

```{r t67e}
source('topic_comments/topic_summary_high_cites.R')
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n
	**Comments**
	\n")
```

This study matches up with my experiences suprisingly well. When I was a grad student back in the 1990s, I felt that work on scientific realism was all around. This was in part because I was reading a lot of philosophy of economics, but it also felt like part of the background that everyone should know about. Since then it had seemed less and less relevant to what was going on around me. I had always thought this said more about the changes in my environment than in philosophy at large. I assumed, that is, that there were still just as many discussions about scientific realism going on, but changes in my reading habits meant I wasn't seeing them as much.

Nope! This topic really has fallen away quite a bit from the 1990s. Or, at least, it has really fallen away in these twelve journals. I expect if you looked at a broader range of journals you'd see a different story. But scientific realism has become a smaller topic in the twelve journals I'm looking at.

You don't need a fancy model to see this. You can see it too in the raw word counts. This is helpful because it lets us cross test the output of the fancy model. It's not helpful to look at how often the word 'realism' is used, since this has so many different meanings. But we can look at some of the names most associated with this debate to get a sense of how often the debate was taking place in the pages of these journals

```{r realism-names}
word_frequency_graphs(c("laudan", "kuhn", "boyd", "lakatos"))
```

There is a lot of year to year variation there, but the basic pattern that things rise pretty quickly through the 1980s, and then fall away just as quickly after that, seems fairly clear. In the 1990s when I was reading this stuff, it was a debate running out of steam. 

As one other aside, I'm surprised that the raw counts for 'Kuhn' and 'Boyd' are so low. For one thing, those names belong to more people than their most famous owners. For another I thought 'Boyd' might have more of a boost from being at Cornell, even in the _Philosophical Review_. For another, 'Kuhn' is much lower than other similarly famous figures of the third quarter of the twentieth century.

```{r mid-century-american-names}
word_frequency_graphs(c("quine", "kuhn", "rawls", "kripke"))
```

There are years when the word 'Rawls' is being used about once every thousand words. That's once every 2-3 pages over all 12 journals! But 'Kuhn' only once gets above once every five thousand words, and then only barely.