```{r t24a}
jjj <- 24
source('topic_summary_data.R')
opts_knit$set(eval.after = "fig.cap")
```

```{r t24b, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal")}
#source('topic_summary_facet_graph.R')
# The graphs blow up here, so we're increasing the upper bound
yupper <- max(filter(journalgamma_frequency, topic == jjj)$gamfre, 0.3, na.rm=TRUE)

facet_labels <- chap_two_facet_labels %>%
  mutate(year = 1944.5, gamfre = yupper)

facet_labels$journal <- factor(facet_labels$journal, levels = journal_order)

indiv_journal_graphs <- ggplot(data = filter(journalgamma_frequency, topic == jjj) %>% drop_na(), aes(x = year, y = gamfre))  +
  theme(legend.position="none") +
  coord_cartesian(ylim=c(0, yupper), expand = TRUE) +
  scale_y_continuous(breaks = c(0.1,0.2)) +
  labs(x = "Year", y = "Weighted Proportion of Articles", title = the_categories$subject[jjj]) +
  theme_minimal() +
  theme(plot.title = element_text(size = rel(1), 
                                  face = "bold",
                                  colour = hcl(h = (jjj-1)*(360/cats)+15, l = 65, c = 100),
                                  margin = margin(0, 0, 5, 0)),
        strip.text = element_blank(),
        panel.spacing.x = unit(0.3, "lines"),
        panel.background = element_blank(),
        panel.spacing.y = unit(0.4, "lines"),
        axis.title.x = element_text(size = rel(1)),
        axis.title.y = element_text(size = rel(1)),
        panel.grid.major = element_line(color = "grey85", size = 0.08),
        panel.grid.minor = element_line(color = "grey88", size = 0.05),
        legend.position="none") +
  geom_point(size = 0.2, colour = hcl(h = (jjj-1)*(360/cats)+15, l = 65, c = 100)) + 
  facet_wrap(~journal, ncol = 3, labeller = as_labeller(journal_short_names)) +
  geom_text(data = facet_labels,
            mapping = aes(label = short_name),
            vjust = "inward", 
            hjust = "middle",
            fontface = "bold", 
            size = 3,
            colour = "grey40")
print(indiv_journal_graphs)
```

```{r t24c, fig.cap=the_categories$subject[jjj], fig.height= 5.2}
cat("<br>")
source('topic_summary_overall_graph.R')
```

```{r t24d}
cat("<br>")
source('topic_summary_char_art.R')
temp_dt
```

```{r t24e}
cat("<br>")
source('topic_summary_high_cites.R')
if(is_high_cites == 1)
	{cat("<br>")}
if(is_high_cites == 1)
	{high_table}
if(is_high_cites == 1)
	{cat("<br>")}
cat("\n
	**Comments**
	\n")
```

Note I had to change the scales here, especially because of the Aristotelian Society.

Compare max values for different journals.

Note that there are 30 highly cited articles. Bernard Williams, Frank Jackson, Stephen Yablo, Philippa Foot. Kind of good writers. (Though also Wittgenstein, so shrug emoji.)

Binary sort

Not actually a subject, more a style. Look at the keywords. Maybe do the keyword graphs. And maybe even facet the graph for surely, certainly, perhaps, quite.

It is driven a lot by Aristotelian Society. But stays at 10% of PR for years (maybe Malcolm's influence). Never really catches on a J Phil, and especially at BJPS. Going up and up at PPR and Ethics.

Advice to young players: stop word out a bunch of these words.