```{r t58a}
jjj <- 58
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t58b, fig.cap=paste0(fcap(the_categories$sub_lower[jjj]),"."),  fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t58c, fig.cap=paste(fcap(the_categories$sub_lower[jjj]), "articles in each journal."), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t58d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t58e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

This is another topic that came in a little smaller than I expected, perhaps in part because the model was construing it slightly more narrowly than I was. I certainly would have guessed that articles about minds and machines would be much more than 0.6–0.8 percent of the articles.

The explanation here is that the topic got squeezed from all sides. There are topics about [physicalism](#topic09), [conceivability arguments](#topic55), [wide content](#topic85) and [cognitive science](#topic87). What's left here are articles on a very specific range of arguments about whether minds are best thought of as machines. Put that way, the real surprise is that it hasn't faded more. There is a small downward trajectory towards the right-hand edge, but only a small one. Issues that Turing, Gödel, Searle and others raised continue to fascinate philosophers.