```{r t18a}
jjj <- 18
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t18b, fig.cap=paste0(fcap(the_categories$sub_lower[jjj]),"."),  fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t18c, fig.cap=paste(fcap(the_categories$sub_lower[jjj]), "articles in each journal."), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t18d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t18e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

This one really surprised me. 

It isn't a surprise that there is a topic on mechanisms. "[Thinking About Mechanisms](https://philpapers.org/rec/MACTAM)" is one of the most cited philosophy papers of the last few decades, and it makes sense that it would give rise to a topic.

No, what really surprised me was that there are so many articles in here from so long ago. I thought this would be a very modern topic, really taking off after 2000.

Part of what happens is that there is a series of articles on, broadly speaking, behaviorist psychology that end up here. These start out looking like straightforward philosophy of mind articles, but they move into being something more like psychology or philosophy of psychology articles, and from there it isn't too hard to get to philosophy of biology. And that's basically where the topic ends up, and it's how I've classified it. So it includes papers like "[A Tentative Analysis of the Primary Data of Psychology](https://philpapers.org/rec/KANATA)" [@Kantor1921], which is an attempt to separate out what is meant by stimulus, response and behavior. This is taken to be the crucial foundational question, because these constitute the core psychological data. It's a fairly interesting bit of history, and one that I wasn't at all aware played out in philosophy journals.