```{r t43a}
jjj <- 43
source('topic_summary_data.R')
opts_knit$set(eval.after = "fig.cap")
```

```{r t43b, fig.cap=paste(the_categories$subject[jjj], fig.height= 5.2}
source('topic_summary_overall_graph.R')
```

```{r t43c, fig.cap=the_categories$subject[jjj], "Articles in Each Journal")}
cat("<br>")
source('topic_summary_facet_graph.R')
```

```{r t43d}
cat("<br>")
source('topic_summary_char_art.R')
temp_dt
```

```{r t43e}
cat("<br>")
source('topic_summary_high_cites.R')
if(is_high_cites == 1)
	{cat("<br>")}
if(is_high_cites == 1)
	{high_table}
if(is_high_cites == 1)
	{cat("<br>")}
cat("\n
	**Comments**
	\n")
```

It's basically _On Denoting_.

_Mind_ reprinted _On Denoting_ for its 100th anniversary, and the model provides slightly different probabilities for it. Partially this is because this is a non-deterministic model, and partially it's because there was a little bit of editorial introduction that made it into the 2005 text.

Some of the papers in here are best thought of as history papers. This is one of the challenges with these topics from early analytic work. We're covering such a long range that we include papers that were not at all history papers, like say _On Denoting_, as well as historical work on those papers. But I think it makes much more sense to call this a history topic.

_On Denoting_ is one of the most important papers in the history of analytic philosophy, so it makes sense that it would be a topic of its own, that its importance would be recognised immediately, and that it would lead the citation counts. Except only the first of those three things is true. 

You do see a bit of attention paid to it in 1911 and 1912 - there is an important exchange between Russell and [Emily Elizabeth Constance Jones](https://plato.stanford.edu/entries/emily-elizabeth-constance-jones/) - but then it is basically invisible from the start of World War One to the end of World War Two. This pattern, Russell writes a super important paper but it only gets proper attention decades later, will repeat itself a bit, though this is the paradigm case.

And I was a little surprised which papers are cited more often than _On Denoting_. According to Google, at least, _What Is It Like to Be a Bat?_ has twice its citations. _What Is It Like to Be a Bat?_ is an important paper too, but still this was a bit of a shock.