```{r t22a}
jjj <- 22
source('topic_summary_data.R')
opts_knit$set(eval.after = "fig.cap")
```

```{r t22b, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal")}
source('topic_summary_facet_graph.R')
```

```{r t22c, fig.cap=the_categories$subject[jjj], fig.height= 5.2}
cat("<br>")
source('topic_summary_overall_graph.R')
```

```{r t22d}
cat("<br>")
source('topic_summary_char_art.R')
temp_dt
```

```{r t22e}
cat("<br>")
source('topic_summary_high_cites.R')
if(is_high_cites == 1)
	{cat("<br>")}
if(is_high_cites == 1)
	{high_table}
if(is_high_cites == 1)
	{cat("<br>")}
cat("\n
	**Comments**
	\n")
```

This topic is mid-century philosophy of language, especially influenced by Wittgenstein's later work. It's tempting to say that it's influenced by _Philosophical Investigations_, though as you can see some of this work takes place well before the Investigations are published. Still, a lot of this work turns out to have had a Wittgensteinian influence. 

For example, those high points in the graph for pre-war _Analysis_ are largely driven by a few exchanges. One of those is between Margaret MacDonald, A. M. MacIver on how to understand the type/token distinction. The exchange includes at least the following. (I think this is complete, though I may have missed some.)

- [Language and Reference, by Margaret MacDonald](https://academic-oup-com./analysis/article/4/2-3/33/175389), Analysis, 4 (2/3): 33–41 (1936).
- [Token, Type and Meaning, by A. M. MacIver](https://philpapers.org/rec/MACTTA-2), Analysis 4 (4):58 - 64 (1936).
- [Reply to Mr. MacIver, by Margaret MacDonald](https://philpapers.org/rec/MACRTM-4) Analysis 4 (5):77 - 80 (1937).
- [Rejoinder to Miss MacDonald, by A. M. MacIver](https://philpapers.org/rec/MACRTM-3), Analysis 4 (6):81 - 88 (1937).
- [Further Reply to Mr. MacIver, by Margaret MacDonald](https://philpapers.org/rec/MACFRT-2), Analysis 5 (1):12 - 16 (1937).
- [Last Words to Miss MacDonald, by A. M. MacIver](https://philpapers.org/rec/MACLWT), Analysis 5 (2):28 - 31 (1937).
- [Erratum: Last Words to Miss MacDonald, by A. M. MacIver](https://philpapers.org/rec/MACELW),  Analysis 5 (3/4):64 (1938).

On the one hand, I'm on MacIver's side of the philosophical dispute here. On the other hand, you could put his articles in a museum as an exemplar of mansplaining. So it's an interesting exchange.

MacDonald is notable for several reasons, this exchange not really being one of them. She was one of the founders of _Analysis_, and then edited it from 1948 until her tragically early death in 1956. She wrote a very important paper on natural rights; it is the only highly cited paper back in [Topic 3](#topic03). And it was her notes, along with those of Alice Ambrose, that got turned into Wittgenstein's _Lectures on Ethics_. So there is a Wittgensteinian influence to these pre-war papers too.

I was surprised that this topic didn't feature more papers in _Philosophical Review_. I thought Norman Malcolm's move to Cornell in 1947 would have led to more Wittgensteinian articles here. But it turns out these mostly ended up in Topic 24.