```{r t78a}
jjj <- 78
source('topic_summary_data.R')
opts_knit$set(eval.after = "fig.cap")
```

```{r t78b, fig.cap=the_categories$subject[jjj], fig.height= 5.2}
source('topic_summary_overall_graph.R')
```

```{r t78c, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal")}
cat("<br>")
source('topic_summary_facet_graph.R')
```

```{r t78d}
cat("<br>")
source('topic_summary_char_art.R')
temp_dt
```

```{r t78e}
cat("<br>")
source('topic_summary_high_cites.R')
if(is_high_cites == 1)
	{cat("<br>")}
if(is_high_cites == 1)
	{high_table}
if(is_high_cites == 1)
	{cat("<br>")}
cat("\n
	**Comments**
	\n")
```

Given the importance of Concepts to late twentieth century philosophy, this is a surprisingly small topic. I think that what's happened here is that it has just gotten squeezed by other topics. There isn't a single article that's more than 10 pages long with a probability of being in this topic of over 0.5.

Part of the story about this topic is similar to the story with the topic on [Arguments](#topic55). More philosophers write about concepts in papers on other topics than write papers directly about concepts. This isn't surprising, but it did surprise me a bit that there aren't more papers directly about concepts in the journals. There are several important books on concepts, and there are papers in specialist journals like _Mind and Language_, and that led me to expect that there would be more here than turned out to be the case.

Surprisingly small. Just gets squeezed. Not a single article above 10 pages and above 0.5 probability.