```{r t79a}
jjj <- 79
source('topic_comments/topic_summary_data.R') # Get data
opts_knit$set(eval.after = "fig.cap")
```

```{r t79b, fig.cap=the_categories$subject[jjj], fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t79c, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal")}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t79d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t79e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

This topic would look very different if we ran the study forward a few years. Work on race is distinctive enough that the model wants to put it somewhere on its own, but small enough that it needs supplementing with other work to get to be a topic. Even with supplementation, it's the smallest topic (by weighted sum) of the 90. That would not be the case if we ran the study through 2020, I'm sure.

Putting together papers about DNA with papers about race isn't the strangest thing the model has done. (Though it is a little random; this wasn't a common pairing.) Even philosophers who deny that DNA has much if anything to do with race will talk why it does not. And the model is just tracking word associations. If everyone is talking about why X and Y aren't connected, the model just sees the words for X and Y turning up a lot in the same papers, and connects them.

I don't really know enough philosophy of biology to know why the biology papers in this topic were split off from the much larger topic of [Evolutionary Biology](#topic82). It looks like a distinction without much of a difference to me, but maybe it's tracking an important topic distinction.