```{r t08a}
jjj <- 8
source('topic_comments/topic_summary_data.R') # Get data
opts_knit$set(eval.after = "fig.cap")
```

```{r t08b, fig.cap=the_categories$subject[jjj], fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t08c, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal")}

source('topic_comments/topic_summary_facet_graph.R')
```

```{r t08d}

source('topic_comments/topic_summary_char_art.R')
temp_dt
```

```{r t08e}
source('topic_comments/topic_summary_high_cites.R')
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n
	**Comments**
	\n")
```

The main striking thing about this topic is how confident the model is that articles from both ends of the timeline belong together. 

```{r bosanquet-aesthetics}
individual_article("10.2307_4543553")
```

```{r dom-aesthetics}
individual_article("10.2307_23012980")
```

It knows that Bosanquet is an idealist, and McIver Lopes is not. But it also knows that despite that, they have a subject matter in common. This isn't something you see for many other topics. The same thing happens with the [Temporal Paradoxes](#topic19) and, to a lesser extent, with [Colour](#topic40). But it is particularly marked here.