```{r t32a}
jjj <- 32
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t32b, fig.cap=the_categories$subject[jjj], fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t32c, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal"), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t32d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t32e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

Another fairly easy topic to describe - it's Kant. Both Kantian ethics and Kantian metaphysics end up here. Like all of the other early modern topics, it drops away a bit after Ryle takes over _Mind_ and decrees that only Greek history will be allowed in the journal. But it always hovers a bit above the zero line.

I had expected there would be a bit more in recent years, but I think I'd been taking _Philosophical Review_ to be a more representative than it turns out to be. The data is a little noisy, but it does look like _Philosophical Review_ has been substantially more receptive to work on Kant in the last twenty years than any of the other journals.
