```{r t38a}
jjj <- 38
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t38b, fig.cap=the_categories$subject[jjj], fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t38c, fig.cap=paste(the_categories$subject[jjj], "articles in each journal."), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t38d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t38e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

A tiny topic, but still one that seemed to need breaking up in order to categorise. The papers are mostly about origins and ends, which make sense as a unified category. But then it bifurcates into debates within metaphysics, primarily about essentialism and identity over time, and in philosophy of science, about the role of teleological reasoning. 

There are only ninety articles here, so there isn't a ton to say about them collectively. It was a little surprising to me that there isn't a Kripke/Parfit-related bump in the 1970s for work on personal identity, especially since so much of the work is on origin essentialism. Part of the story is that there is a bit of work in the British journals on personal identity before the Kripke/Parfit boom, some of it inspired by Wiggins. And the topic is small enough that that's enough to stop a huge rise once Kripkean and Parfittian theories of personal identity become prominent.
