```{r t13a}
jjj <- 13
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t13b, fig.cap=the_categories$subject[jjj], fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t13c, fig.cap=paste(the_categories$subject[jjj], "articles in each journal."), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t13d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t13e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

One of the reasons I ended up with ninety topics was because when I ran this model with sixty to seventy-five topics, it kept putting a weird subset of the Plato papers in with other topics. This was odd because  sorting the ancient philosophy papers neatly together was something that just about every other model run did perfectly. And I thought it should be easy for this one too, if I just bumped up the number of topics a bit. And eventually it happened. I kind of expected that I'd have more models that separated Aristotle from Plato, but I don't think I ever saw that.

The publication numbers are much as I expected. The raw numbers outrun the weighted numbers, which is possibly surprising. If there was more name checking of ancient philosophy in contemporary works—meaning there were a bunch of things that are not really ancient philosophy papers but which had just enough ancient philosophy to confuse the model—it would be the other way around. But the model knows that the word _platonism_ in a metaphysics or philosophy of math paper doesn't mean we're maybe doing ancient philosophy.

Still, it does end up being twenty-fifth of the ninety topics. Given the relative importance of books to papers in ancient philosophy, and the complete lack of interest in ancient philosophy from some of these journals, I feared it could be lower than this.