```{r t15}
jjj <- 15
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t15b, fig.cap=the_categories$subject[jjj], fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t15c, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal"), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t15d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t15e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

This is one of the main places in the model we see logical positivism: a sustained discussion from about 1936 (the publication of _Language, Truth and Logic_) to 1980 of the verification principle. It feels to me like this model really gets going when the problems for the verification principle are most pressing - many of these articles are about problems for, and the rapidly diminishing probability of salvaging, the verification principle. For instance, the second highest probability the model gives to an article being in this topic is Robert Brown and John Watling's [Amending the Verification Principle](https://philpapers.org/rec/BROATV) [@BrownWatling1951], which as early as 1951 is already deep into the 'one patch per puncture' approach to saving the principle.

The model didn't quite know what to do with papers about conditionals in general. I'll talk about them more in what follows, because they are a tricky problem. But it turns out a bunch of pre-Lewisian papers on subjunctive conditionals ended up here as well. That's not surprising; they are a particularly tricky problem for verificationists to handle.