```{r t74a}
jjj <- 74
source('topic_comments/topic_summary_data.R') # Get data
opts_knit$set(eval.after = "fig.cap")
```

```{r t74b, fig.cap=the_categories$subject[jjj], fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t74c, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal")}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t74d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t74e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

It's perhaps a bit surprising that theory of knowledge - everything from scepticism to Gettier cases to testimony to closure principles to Williamsonian knowledge first epistemology - is in just one topic. And that it's just 1.3% of all the articles.

In part this is because of how new a topic it is. There just isn't very much that feels like contemporary epistemology from before World War II. Of the 426 articles in this topic, only 6 of them are between World War II. And five of those feel like fairly borderline cases, where the model couldn't really make up its mind. There is one notable exception.

```{r testimony-article}
individual_article("10.2307_2249544")
```

I couldn't find any other references to **Dhirendon** Mohon Datta, but that's a typo. (Or a non-standard transliteration.) **Dhirendra** Mohan Datta wrote a number of books. (The details about Datta that follow are from sources that I was pointed to in helpful conversations with Michael Bench-Capon, Bryce Huebner and Michael Kremer.)

He wrote [The Philosophy of Mahatma Ghandi](https://www.amazon.com/Philosophy-Mahatma-Gandhi-Dhirendra-Mohan/dp/0299010147) [@Datta1953], based on his time working with Ghandi. 

He also wrote [The Six Ways of Knowing: A Critical Study of the VedÄnta Theory of Knowing](https://archive.org/details/TheSixWaysOfKnowing1960D.M.Datta/mode/2up) [@Datta1960], which overlaps with this paper. Indeed, on page 337 of the second edition of that book, he refers to "Testimony as a Method of Knowing" as his article. (Thanks to Michael Bench-Capon for spotting this.) I've linked to the second edition, which is the only one I could find online. If the first edition is like the second, it would be decades ahead of its time. (And the _Mind_ article suggests that that's true.)

And he co-authored a prominent textbook: [An Introduction to Indian Philosophy](https://www.amazon.com/dp/B01C2IHREY/ref=dp-kindle-redirect) [@ChatterjeeDatta].

When he retired, Datta's colleagues and students put together a festschrift for him, which is available through the Internet Archive: [World Perspectives in Philosophy, Religion and Culture](https://archive.org/details/in.ernet.dli.2015.126145/page/n7/mode/2up) [@Singh1960]. These books normally have a somewhat detailed biography of the honoree, but this one only has a skimpy four page stub. Still, we learn something interesting from it. Most of the Indian philosophers who published in _Mind_ and _Philosophical Review_ in the first half of the century spent a fair bit of time in Britain or America.^[Datta also had [an invited paper](https://www.jstor.org/stable/2181796?seq=1#metadata_info_tab_contents) in _Philosophical Review_.] Datta did not; he acquired his very extensive knowledge of philosophy in England from his teachers (especially his brother) and his own reading.

There is a really interesting book to be written about the ways in which late twentieth century English language philosophy resembles (some strands in) Indian philosophy more than it resembles early twentieth century English language philosophy. And Datta could be a key part of that story. But that's for another book and, preferably, an author with more knowledge of Indian philosophy than I have. So I'll leave Datta here for now.

I've written much more on post-war epistemology in chapter \@ref(epistemologychapter). The main takeaway from the longer chapter is that work on "Gettier cases" makes up a surprisingly small amount of the work in epistemology. It does make up a large percentage of the work in epistemology in the early years. (And for epistemology, the early years extend into the 1980s.) But it's never as big a percentage of work done in philosophy as I suspect a lot of people believe.