```{r t81a}
jjj <- 81
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t81b, fig.cap=paste0(fcap(the_categories$sub_lower[jjj]),"."),  fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t81c, fig.cap=paste(fcap(the_categories$sub_lower[jjj]), "articles in each journal."), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t81d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t81e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

This includes a bunch of relatively modern work on the nature of reasons, the nature of desires, and the interaction between them. This could say more about me than about the model, but I was surprised this topic wasn't both bigger and later. It isn't small—either the thirty-second or thirty-third largest depending on which measure is used. But plenty of model runs had a topic centered on reasons as the latest topic to appear, and having nine topics come after it was not something I saw in many runs. What happened here, I think, was that this model was more inclusive than other models I ran at including 1970s work (like the Watson and Wiggins articles in the highly cited list), but also split off some papers into the [norms topic](#topic90) that could have been here.

One nice thing is that the model seems to have not gotten tricked at all by the terms _internalism_ and _externalism_. I would have thought they would have thrown it for a loop. But it seems to have been able to figure out that papers about internalism versus externalism about reasons are not the same as papers about internalism versus externalism about justification. This was pleasing and a fairly hard test for the utility of the model in classifying papers.