```{r t30a}
jjj <- 30
source('topic_comments/topic_summary_data.R') # Get data
```

```{r t30b, fig.cap=paste0(fcap(the_categories$sub_lower[jjj]),"."),  fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t30c, fig.cap=paste(fcap(the_categories$sub_lower[jjj]), "articles in each journal."), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t30d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t30e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

I've called this _philosophy of chemistry_, but it could just as easily be described as nonfundamental physics. Any kinds of discussion of physics beyond the most fundamental is a candidate for ending up here.

But note this could easily be merged with the later topic on [thermodynamics](#topic73), which captures a lot of recent work on philosophical issues arising out of the study of entropy. Looking at these graphs gives a slight underestimate of how much time philosophers of physics (broadly construed) spend looking at anything other than maximally fundamental issues in physics. 