```{r t35a}
jjj <- 35
source('topic_comments/topic_summary_data.R') # Get data
opts_knit$set(eval.after = "fig.cap")
```

```{r t35b, fig.cap=the_categories$subject[jjj], fig.alt = alt_text, fig.height= 5.2}
source('topic_comments/topic_summary_overall_graph.R')
```

```{r t35c, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal"), fig.alt = alt_text_journals}
source('topic_comments/topic_summary_facet_graph.R')
```

```{r t35d}
source('topic_comments/topic_summary_char_art.R') # Create table of all articles in topic
temp_dt
```

```{r t35e}
source('topic_comments/topic_summary_high_cites.R') # Generate table of highly cited articles. 
 # Have to do this at same time as previous script or a weird caching error occurs.
if(is_high_cites == 1){high_table} # Conditional because not all topics have high cites
cat("\n

**Comments**
	\n")
```

One of the big fears I had doing this project was that the model would get confused between different uses of the one word. We've already seen the model get confused by terminological changes that don't reflect philosophical changes. But that's not a deep problem; we can just manually add the generated topics back together. But common terminology for the same idea is harder to deal with.

And it's what we have here. This topic includes work on political freedom, and work on free will. It doesn't help that both fields spend a lot of time talking about libertarian views. And it really doesn't help that some people, perhaps not that many but enough to confuse the model, think there are deep connections between the fields.

Fortunately there turns out to be a way to handle this problem. I'll go over this when we get to [Sets and Grue](#topic37), but the short version is that building a two topic LDA out of the articles in this topic lets us more or less split apart the articles on political freedom from the articles on free will.

I've classified the free will papers as ethics, although I think a lot of the people working on the topic would have thought of themselves as doing metaphysics. Certainly when I was a student we covered free will in intro metaphysics classes, not intro ethics classes. But it seems to me this is clearly about ethics, and the recent trend towards looking much more closely at the nature of responsibility, especially in light of empirical discoveries about the mind and brain, makes this classification much more natural.

Note that this is very much not the last we'll hear of free will. There will be an entire topic devoted to Frankfurt cases. And some of the work on responsibility comes up in the several ethics topics. So don't take these graphs as any kind of measure of how much coverage free will gets. 