```{r t82a}
jjj <- 82
source('topic_summary_data.R')
opts_knit$set(eval.after = "fig.cap")
```

```{r t82b, fig.cap=the_categories$subject[jjj], fig.height= 5.2}
source('topic_summary_overall_graph.R')
```

```{r t82c, fig.cap=paste(the_categories$subject[jjj], "Articles in Each Journal")}
cat("<br>")
source('topic_summary_facet_graph.R')
```

```{r t82d}
cat("<br>")
source('topic_summary_char_art.R')
temp_dt
```

```{r t82e}
cat("<br>")
source('topic_summary_high_cites.R')
if(is_high_cites == 1)
	{cat("<br>")}
if(is_high_cites == 1)
	{high_table}
if(is_high_cites == 1)
	{cat("<br>")}
cat("\n
	**Comments**
	\n")
```

This topic is one of the most notable, and one of the most exciting, developments in philosophy in the past few decades. My sense is that one of the reasons this became such a big topic in philosophy is that there was getting to be less and less support within biology departments for the kind of theoretical work about the foundations of evolution that is being done here. Whether that's true or not, large numbers of philosophers have started taking up this work, and the results are impressive.

From the perspective of the model, one striking thing about this topic is the nature of the "Most Cited Articles" list. It isn't the longest such list, though it is well above average. But most of the other topics that have a long list of highly cited articles have many of those articles only loosely connected to the topic. (See topic 24 for the most notable example of that.) It's striking to see so many highly cited articles that the model is more than 50% confident are in one particular topic.

It's easy to think of this as a somewhat 'specialist' topic. Apart from a few articles in _Journal of Philosophy_, pretty much all the work is in the two philosophy of science journals. But I think it's a somewhat parochial view inside philosophy to think of this as the specialized subject. If you walked around a large university, you'd probably find more people who could follow, and were interested in, these papers than you could if you did the same exercise for papers on reasons or on knowledge. It's true that a relatively small percentage of _philosophers_ could follow, or even are interested in following, the papers in this topic. But that might say more about philosophers than about the material.